---
title: "Tontine Stress Test: 1-Year Ladder"
date: "2026-04-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Purpose

This notebook is the orchestration layer for tontine yield-curve stress testing.
Reusable application logic lives in `applications/tontine_helpers.R`; model
logic remains in `yield_estimation/` and `stress_testing/`.

```{r libraries}
library(here)
library(dplyr)
library(purrr)
library(ggplot2)
library(scales)
library(tibble)
library(gridExtra)
library(vars)
library(tsDyn)
library(Matrix)

sys.source(here::here("applications", "tontine_helpers.R"), envir = .GlobalEnv)
tontine_source_project()
```

```{r configuration}
curve_files <- list(
  usa = "usa-bs.csv",
  gbr = "gbr-bs.csv",
  jpn = "jpn-bs.csv",
  ger = "ger-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "usa"

mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- tontine_mat_names(mats)

data_start_date <- as.Date("2010-01-01")
data_end_date <- as.Date("2021-12-31")
lookback_years <- 1

lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)
fit_seed <- 999

mce_baseline_controls <- list(
  ECM_alpha = 0.2,
  X_trunc = TRUE,
  Xt_smooth = FALSE,
  smoother = NULL,
  CR_S0_shrink_diag = 0.4,
  CR_check_every = 10,
  CR_use_loglik = FALSE,
  CR_store_path = FALSE
)

mce_shock_controls <- list(
  reuse_ECM = TRUE,
  reuse_BS0 = TRUE,
  ECM_fallback = "baseline",
  anchor_shock_curves = FALSE
)

purchase_years <- 2011:2020
N_members <- 1000
target_total_ladder_par_per_member <- 100000
target_rung_par_per_member <- target_total_ladder_par_per_member / length(purchase_years)
total_target_par <- N_members * target_total_ladder_par_per_member
population_seed <- fit_seed
q_full <- c(
  0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
  0.021506, 0.023614, 0.025473, 0.027789, 0.030319
)
stopifnot(length(q_full) >= length(purchase_years))
q <- q_full[seq_along(purchase_years)]

baseline_model_names <- c("Observed", "DNS", "DLY", "MCE")
shock_model_names <- c("DNS", "DLY", "MCE")
```

```{r population-simulation}
population_simulation <- tontine_simulate_population(
  N_members = N_members,
  q = q,
  seed = population_seed
)
```

```{r data}
yields <- tontine_read_yields(
  curve_files = curve_files,
  start_date = data_start_date,
  end_date = data_end_date
)
```

```{r valuation-windows}
valuation_windows <- tontine_build_valuation_windows(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = purchase_years,
  lookback_years = lookback_years
)
```

```{r ladder-schedule}
ladder_schedule <- tontine_build_bond_ladder_schedule(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = purchase_years,
  curves = curves,
  total_target_par = total_target_par,
  q = q,
  population_simulation = population_simulation,
  target_rung_par_per_member = target_rung_par_per_member
)
```

```{r baseline-models}
set.seed(fit_seed)

baseline_curve_models <- tontine_fit_rolling_baseline_curve_models(
  yields = yields,
  valuation_windows = valuation_windows,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  mce_controls = mce_baseline_controls,
  include_models = baseline_model_names,
  fit_seed = fit_seed
)
```

```{r baseline-valuation}
baseline_valuation <- tontine_price_baseline_models(
  baseline_curve_models = baseline_curve_models,
  ladder_schedule = ladder_schedule,
  mat_names = mat_names
)

baseline_country_holdings <- baseline_valuation$country_holdings
baseline_cash_accounts <- baseline_valuation$cash_accounts
baseline_model_summary <- tontine_summarize_baseline_ladder(baseline_valuation)
```

## Shock Examples

The first two examples target the 2015 purchase rung. With the current one-year
rolling setup, that means the valuation window ending on the first observed
2015 reference-curve date. Those shocks are applied over the full rows supplied
to that window's model fit; all other rungs use their unshocked rolling fits.

The third example is a cross-window shock profile. It begins at the 2015
purchase date with a `-1.0` USA level-factor shock and then linearly decays to
zero at the 2020 purchase date. Each rolling model fit receives whatever portion
of that calendar shock profile overlaps its annual valuation window.

- `USA L -100 BPS`: additive level-factor shock of `-1.0` to the USA curve.
- `GBR + GER L -100 BPS`: simultaneous additive level-factor shock of `-1.0`
  to the GBR and GER curves, while USA remains the reference curve.
- `USA L -100 BPS linear decay 2015-2020`: additive level-factor shock of
  `-1.0` to the USA curve beginning at the 2015 purchase date, linearly decaying
  to `0.0` by the 2020 purchase date.

These shock valuations are reported only for `DNS`, `DLY`, and
`MCE`. The observed curves remain a baseline diagnostic; directly shocking the
observed curves is not an informative model comparison.

```{r shock-specs}
shock_examples <- list(
  usa_l_neg100bps_2015 = list(
    label = "2015 USA L -100 BPS",
    shock_year = 2015,
    shock_curves = "usa",
    shock_factors = "L",
    shock_magnitude = -1.0,
    shock_type = "additive",
    shock_window = NULL,
    shock_window_position = "first"
  ),
  gbr_ger_l_neg100bps_2015 = list(
    label = "2015 GBR+GER L -100 BPS",
    shock_year = 2015,
    shock_curves = c("gbr", "ger"),
    shock_factors = "L",
    shock_magnitude = -1.0,
    shock_type = "additive",
    shock_window = NULL,
    shock_window_position = "first"
  ),
  usa_l_neg100bps_decay_2015_2020 = list(
    label = "USA L -100 BPS linear decay 2015-2020",
    shock_profile = "linear_decay",
    shock_start_year = 2015,
    shock_start_anchor = "purchase_date",
    shock_end_year = 2020,
    shock_end_anchor = "purchase_date",
    shock_curves = "usa",
    shock_factors = "L",
    shock_start_magnitude = -1.0,
    shock_end_magnitude = 0.0,
    shock_type = "additive"
  )
)
```

```{r shock-valuations}
shock_curve_models <- purrr::imap(shock_examples, function(shock_spec, shock_key) {
  tontine_fit_rolling_shocked_curve_models(
    yields = yields,
    valuation_windows = valuation_windows,
    curves = curves,
    mats = mats,
    mat_names = mat_names,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference_curve = reference_curve,
    shock_spec = shock_spec,
    mce_controls = mce_baseline_controls,
    mce_shock_controls = mce_shock_controls,
    include_models = shock_model_names,
    fit_seed = fit_seed
  )
})

shock_valuations <- purrr::imap(shock_curve_models, function(curve_models, shock_key) {
  tontine_price_baseline_models(
    baseline_curve_models = curve_models,
    ladder_schedule = ladder_schedule,
    mat_names = mat_names,
    scenario_type = "shock",
    scenario_name_prefix = shock_examples[[shock_key]]$label,
    shock_label = shock_examples[[shock_key]]$label,
    initial_cash = baseline_valuation$initial_cash
  )
})
```

```{r shock-summaries}
tontine_summarize_rungs <- function(valuation) {
  valuation$country_holdings %>%
    dplyr::group_by(model, scenario, scenario_type, shock_label, rung_id, purchase_year) %>%
    dplyr::summarise(
      average_1y_zero_rate = mean(zero_rate_1y),
      total_purchase_cost = sum(purchase_cost),
      total_maturity_proceeds = sum(maturity_proceeds),
      .groups = "drop"
    ) %>%
    dplyr::left_join(
      valuation$cash_accounts %>%
        dplyr::select(model, scenario, rung_id, cash_end, rung_profit_loss, cumulative_profit_loss),
      by = c("model", "scenario", "rung_id")
    )
}

baseline_rung_summary <- tontine_summarize_rungs(baseline_valuation)

shock_model_summaries <- purrr::imap_dfr(shock_valuations, function(valuation, shock_key) {
  shock_label <- shock_examples[[shock_key]]$label
  tontine_summarize_baseline_ladder(valuation) %>%
    dplyr::mutate(shock_key = shock_key, shock_label = shock_label)
})

shock_rung_summaries <- purrr::imap_dfr(shock_valuations, function(valuation, shock_key) {
  tontine_summarize_rungs(valuation) %>%
    dplyr::mutate(shock_key = shock_key)
})

shock_affected_years <- function(shock_spec) {
  if (identical(shock_spec$shock_profile, "linear_decay")) {
    return(seq.int(shock_spec$shock_start_year, shock_spec$shock_end_year))
  }

  shock_spec$shock_year
}

shock_affected_year_lookup <- purrr::imap_dfr(shock_examples, function(shock_spec, shock_key) {
  tibble::tibble(
    shock_key = shock_key,
    purchase_year = shock_affected_years(shock_spec)
  )
})

shock_rung_deltas <- shock_rung_summaries %>%
  dplyr::left_join(
    baseline_rung_summary %>%
      dplyr::select(
        model, rung_id, purchase_year,
        baseline_average_1y_zero_rate = average_1y_zero_rate,
        baseline_total_purchase_cost = total_purchase_cost,
        baseline_cash_end = cash_end,
        baseline_rung_profit_loss = rung_profit_loss
      ),
    by = c("model", "rung_id", "purchase_year")
  ) %>%
  dplyr::mutate(
    delta_average_1y_zero_rate = average_1y_zero_rate - baseline_average_1y_zero_rate,
    delta_total_purchase_cost = total_purchase_cost - baseline_total_purchase_cost,
    delta_cash_end = cash_end - baseline_cash_end,
    delta_rung_profit_loss = rung_profit_loss - baseline_rung_profit_loss
  ) %>%
  dplyr::distinct(shock_key, shock_label, model, rung_id, purchase_year, .keep_all = TRUE)

shock_rung_deltas_affected <- shock_rung_deltas %>%
  dplyr::inner_join(
    shock_affected_year_lookup,
    by = c("shock_key", "purchase_year")
  )

shock_rung_summaries_affected <- shock_rung_summaries %>%
  dplyr::inner_join(
    shock_affected_year_lookup,
    by = c("shock_key", "purchase_year")
  ) %>%
  dplyr::distinct(shock_key, shock_label, model, rung_id, purchase_year, .keep_all = TRUE)

shock_model_summaries

shock_rung_summaries_affected %>%
  dplyr::filter(purchase_year == 2015)

shock_rung_deltas_affected %>%
  dplyr::filter(purchase_year == 2015)
```

```{r summaries}
valuation_windows
baseline_model_summary
baseline_cash_accounts
```

```{r diagnostics}
baseline_country_holdings %>%
  dplyr::group_by(model, rung_id) %>%
  dplyr::summarise(
    average_1y_zero_rate = mean(zero_rate_1y),
    total_purchase_cost = sum(purchase_cost),
    total_maturity_proceeds = sum(maturity_proceeds),
    .groups = "drop"
  )
```

## Visualizations

```{r visualization-data}
model_levels <- c("Observed", "DNS", "DLY", "MCE")
model_palette <- c(
  Observed = "#7E6A9E",
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)
shock_model_palette <- model_palette[shock_model_names]
scenario_levels <- c(
  "Baseline",
  "2015 USA L -100 BPS",
  "2015 GBR+GER L -100 BPS",
  "USA L -100 BPS linear decay 2015-2020"
)
scenario_palette <- c(
  Baseline = "#8A8A8A",
  `2015 USA L -100 BPS` = "#59A14F",
  `2015 GBR+GER L -100 BPS` = "#4C78A8",
  `USA L -100 BPS linear decay 2015-2020` = "#C94C4C"
)

baseline_plot_data <- baseline_rung_summary %>%
  dplyr::mutate(
    model = factor(model, levels = model_levels),
    scenario_label = "Baseline"
  )

shock_plot_data <- shock_rung_summaries_affected %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::group_by(shock_key, shock_label, model, purchase_year) %>%
  dplyr::summarise(
    rung_profit_loss = mean(rung_profit_loss),
    cumulative_profit_loss = mean(cumulative_profit_loss),
    cash_end = mean(cash_end),
    total_purchase_cost = mean(total_purchase_cost),
    total_maturity_proceeds = mean(total_maturity_proceeds),
    average_1y_zero_rate = mean(average_1y_zero_rate),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    scenario_label = shock_label
  )

shock_delta_plot_data <- shock_rung_deltas_affected %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::group_by(shock_key, shock_label, model, purchase_year) %>%
  dplyr::summarise(
    delta_average_1y_zero_rate = mean(delta_average_1y_zero_rate),
    delta_total_purchase_cost = mean(delta_total_purchase_cost),
    delta_cash_end = mean(delta_cash_end),
    delta_rung_profit_loss = mean(delta_rung_profit_loss),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    scenario_label = shock_label
  )

ending_cash_plot_data <- dplyr::bind_rows(
  baseline_model_summary %>%
    dplyr::filter(.data$model %in% shock_model_names) %>%
    dplyr::mutate(scenario_label = "Baseline"),
  shock_model_summaries %>%
    dplyr::mutate(scenario_label = shock_label)
) %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    scenario_label = factor(scenario_label, levels = scenario_levels)
  )

terminal_cash_uplift_data <- shock_model_summaries %>%
  dplyr::left_join(
    baseline_model_summary %>%
      dplyr::select(model, baseline_ending_cash_balance = ending_cash_balance),
    by = "model"
  ) %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    scenario_label = factor(shock_label, levels = scenario_levels),
    terminal_cash_uplift = ending_cash_balance - baseline_ending_cash_balance
  )

baseline_country_plot_data <- baseline_country_holdings %>%
  dplyr::group_by(model, country, rung_id, purchase_year) %>%
  dplyr::summarise(
    country_purchase_cost = sum(purchase_cost),
    country_maturity_proceeds = sum(maturity_proceeds),
    country_bond_profit_loss = country_maturity_proceeds - country_purchase_cost,
    .groups = "drop"
  ) %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

shock_country_summaries <- purrr::imap_dfr(shock_valuations, function(valuation, shock_key) {
  valuation$country_holdings %>%
    dplyr::group_by(model, shock_label, country, rung_id, purchase_year) %>%
    dplyr::summarise(
      country_purchase_cost = sum(purchase_cost),
      country_maturity_proceeds = sum(maturity_proceeds),
      country_bond_profit_loss = country_maturity_proceeds - country_purchase_cost,
      .groups = "drop"
    ) %>%
    dplyr::mutate(shock_key = shock_key)
})

shock_country_delta_plot_data <- shock_country_summaries %>%
  dplyr::left_join(
    baseline_country_plot_data %>%
      dplyr::select(
        model, country, rung_id, purchase_year,
        baseline_country_bond_profit_loss = country_bond_profit_loss
      ),
    by = c("model", "country", "rung_id", "purchase_year")
  ) %>%
  dplyr::mutate(
    delta_country_bond_profit_loss =
      country_bond_profit_loss - baseline_country_bond_profit_loss
  ) %>%
  dplyr::inner_join(
    shock_affected_year_lookup,
    by = c("shock_key", "purchase_year")
  ) %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::group_by(shock_key, shock_label, model, country, purchase_year) %>%
  dplyr::summarise(
    country_bond_profit_loss = mean(country_bond_profit_loss),
    baseline_country_bond_profit_loss = mean(baseline_country_bond_profit_loss),
    delta_country_bond_profit_loss = mean(delta_country_bond_profit_loss),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    scenario_label = shock_label
  )

build_1yr_shock_rung_plot <- function(plot_data, scenario_label) {
  filtered_plot_data <- plot_data %>%
    dplyr::filter(.data$scenario_label == .env$scenario_label)

  out <- ggplot2::ggplot(
    filtered_plot_data,
    ggplot2::aes(x = purchase_year, y = rung_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = TRUE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::scale_x_continuous(breaks = purchase_years) +
    ggplot2::labs(
      title = paste("Shocked Bond P/L by Rung:", scenario_label),
      x = "Purchase Year",
      y = "Rung Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()

  if (dplyr::n_distinct(filtered_plot_data$purchase_year) > 1) {
    out <- out + ggplot2::geom_line(linewidth = 0.8)
  }

  out
}

build_1yr_shock_delta_plot <- function(plot_data, scenario_label) {
  filtered_plot_data <- plot_data %>%
    dplyr::filter(.data$scenario_label == .env$scenario_label)

  out <- ggplot2::ggplot(
    filtered_plot_data,
    ggplot2::aes(x = purchase_year, y = delta_rung_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = TRUE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::scale_x_continuous(breaks = purchase_years) +
    ggplot2::labs(
      title = paste("Incremental Shock Effect on Rung Bond P/L:", scenario_label),
      x = "Purchase Year",
      y = "Change in Rung Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()

  if (dplyr::n_distinct(filtered_plot_data$purchase_year) > 1) {
    out <- out + ggplot2::geom_line(linewidth = 0.8)
  }

  out
}

build_1yr_terminal_cash_plot <- function(plot_data, scenario_label) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$scenario_label == .env$scenario_label),
    ggplot2::aes(x = model, y = terminal_cash_uplift, fill = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_col(width = 0.7, show.legend = FALSE) +
    ggplot2::scale_fill_manual(values = shock_model_palette, drop = TRUE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = paste("Terminal Cash Uplift Versus Baseline:", scenario_label),
      x = "Model",
      y = "Ending Cash Change"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_country_baseline_plot <- function(plot_data, country_name) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$country == .env$country_name),
    ggplot2::aes(x = purchase_year, y = country_bond_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = TRUE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::scale_x_continuous(breaks = purchase_years) +
    ggplot2::labs(
      title = paste("Baseline Country Bond P/L:", toupper(country_name)),
      x = "Purchase Year",
      y = "Country Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_country_shock_delta_plot <- function(plot_data, scenario_label, country_name) {
  filtered_plot_data <- plot_data %>%
    dplyr::filter(
      .data$scenario_label == .env$scenario_label,
      .data$country == .env$country_name
    )

  out <- ggplot2::ggplot(
    filtered_plot_data,
    ggplot2::aes(x = purchase_year, y = delta_country_bond_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = TRUE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::scale_x_continuous(breaks = purchase_years) +
    ggplot2::labs(
      title = paste("Country Shock Effect:", toupper(country_name), scenario_label),
      x = "Purchase Year",
      y = "Change in Country Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()

  if (dplyr::n_distinct(filtered_plot_data$purchase_year) > 1) {
    out <- out + ggplot2::geom_line(linewidth = 0.8)
  }

  out
}

shock_scenario_labels <- vapply(shock_examples, `[[`, character(1), "label")

terminal_cash_uplift_usa_plot <- build_1yr_terminal_cash_plot(
  terminal_cash_uplift_data,
  shock_scenario_labels[["usa_l_neg100bps_2015"]]
)
terminal_cash_uplift_gbr_ger_plot <- build_1yr_terminal_cash_plot(
  terminal_cash_uplift_data,
  shock_scenario_labels[["gbr_ger_l_neg100bps_2015"]]
)
terminal_cash_uplift_decay_plot <- build_1yr_terminal_cash_plot(
  terminal_cash_uplift_data,
  shock_scenario_labels[["usa_l_neg100bps_decay_2015_2020"]]
)

country_baseline_plots <- setNames(lapply(curves, function(country_name) {
  build_1yr_country_baseline_plot(baseline_country_plot_data, country_name)
}), curves)

country_shock_delta_plots <- purrr::imap(shock_scenario_labels, function(scenario_label, shock_key) {
  setNames(lapply(curves, function(country_name) {
    build_1yr_country_shock_delta_plot(
      shock_country_delta_plot_data,
      scenario_label,
      country_name
    )
  }), curves)
})
```

```{r plot-baseline-rung-pl}
ggplot2::ggplot(
  baseline_plot_data,
  ggplot2::aes(x = purchase_year, y = rung_profit_loss, color = model)
) +
  ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
  ggplot2::geom_line(linewidth = 0.8) +
  ggplot2::geom_point(size = 1.8) +
  ggplot2::scale_color_manual(values = model_palette, drop = TRUE) +
  ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
  ggplot2::scale_x_continuous(breaks = purchase_years) +
  ggplot2::labs(
    title = "Baseline Bond P/L by Rung",
    x = "Purchase Year",
    y = "Rung Bond P/L",
    color = "Model"
  ) +
  ggplot2::theme_minimal()
```

```{r plot-baseline-cumulative-pl}
ggplot2::ggplot(
  baseline_plot_data,
  ggplot2::aes(x = purchase_year, y = cumulative_profit_loss, color = model)
) +
  ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
  ggplot2::geom_line(linewidth = 0.8) +
  ggplot2::geom_point(size = 1.8) +
  ggplot2::scale_color_manual(values = model_palette, drop = TRUE) +
  ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
  ggplot2::scale_x_continuous(breaks = purchase_years) +
  ggplot2::labs(
    title = "Baseline Cumulative Bond P/L",
    x = "Purchase Year",
    y = "Cumulative Bond P/L",
    color = "Model"
  ) +
  ggplot2::theme_minimal()
```

```{r plot-shock-rung-pl-usa}
build_1yr_shock_rung_plot(shock_plot_data, shock_scenario_labels[["usa_l_neg100bps_2015"]])
```

```{r plot-shock-rung-pl-gbr-ger}
build_1yr_shock_rung_plot(shock_plot_data, shock_scenario_labels[["gbr_ger_l_neg100bps_2015"]])
```

```{r plot-shock-rung-pl-decay}
build_1yr_shock_rung_plot(shock_plot_data, shock_scenario_labels[["usa_l_neg100bps_decay_2015_2020"]])
```

```{r plot-shock-delta-rung-pl-usa}
build_1yr_shock_delta_plot(shock_delta_plot_data, shock_scenario_labels[["usa_l_neg100bps_2015"]])
```

```{r plot-shock-delta-rung-pl-gbr-ger}
build_1yr_shock_delta_plot(shock_delta_plot_data, shock_scenario_labels[["gbr_ger_l_neg100bps_2015"]])
```

```{r plot-shock-delta-rung-pl-decay}
build_1yr_shock_delta_plot(shock_delta_plot_data, shock_scenario_labels[["usa_l_neg100bps_decay_2015_2020"]])
```

```{r plot-ending-cash}
ggplot2::ggplot(
  ending_cash_plot_data,
  ggplot2::aes(x = model, y = ending_cash_balance, fill = scenario_label)
) +
  ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.78), width = 0.7) +
  ggplot2::scale_fill_manual(
    values = scenario_palette,
    breaks = scenario_levels,
    drop = FALSE
  ) +
  ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
  ggplot2::labs(
    title = "Ending Cash Balance by Scenario",
    x = "Model",
    y = "Ending Cash Balance",
    fill = "Scenario"
  ) +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 30, hjust = 1))
```

```{r plot-terminal-cash-uplift-usa}
terminal_cash_uplift_usa_plot
```

```{r plot-terminal-cash-uplift-gbr-ger}
terminal_cash_uplift_gbr_ger_plot
```

```{r plot-terminal-cash-uplift-decay}
terminal_cash_uplift_decay_plot
```

```{r plot-terminal-cash-uplift-grid, fig.width=16, fig.height=4}
gridExtra::grid.arrange(
  terminal_cash_uplift_usa_plot,
  terminal_cash_uplift_gbr_ger_plot,
  terminal_cash_uplift_decay_plot,
  nrow = 1,
  ncol = 3
)
```

```{r plot-country-baseline-usa}
country_baseline_plots$usa
```

```{r plot-country-shock-delta-usa}
country_shock_delta_plots$usa_l_neg100bps_2015$usa
```

```{r plot-country-shock-delta-gbr}
country_shock_delta_plots$gbr_ger_l_neg100bps_2015$gbr
```

```{r exports, eval=FALSE}
# TODO: write selected tables and artifacts to tmp/tontine/<run_id>/.
```
