---
title: "Tontine Stress Test: Multi-Year Baseline Reinvestment Pool"
date: "2026-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 4.32,
  dpi = 150
)
```

## Purpose

This notebook evaluates baseline closed-pool tontine reinvestment strategies
using 5-year and 10-year zero-coupon bond holdings. The mortality and
withdrawal event path is identical to the 1-year tontine notebook. Initial pool
cash is staged into annual rungs until the ladder is seeded; maturity proceeds
are fully reinvested when they arrive inside the modeled horizon.

Shock scenarios revalue the fixed baseline holdings under global positive
level-factor shocks.

```{r libraries}
library(here)
library(dplyr)
library(purrr)
library(ggplot2)
library(scales)
library(tibble)
library(vars)
library(tsDyn)
library(Matrix)

sys.source(here::here("applications", "tontine_helpers.R"), envir = .GlobalEnv)
sys.source(here::here("applications", "tontine_setup.R"), envir = .GlobalEnv)
tontine_source_project()
```

```{r configuration}
curve_files <- list(
  usa = "usa-bs.csv",
  gbr = "gbr-bs.csv",
  jpn = "jpn-bs.csv",
  ger = "ger-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "usa"

mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- tontine_mat_names(mats)

data_start_date <- as.Date("2010-01-01")
data_end_date <- as.Date("2021-12-31")
lookback_years <- 1

lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)
fit_seed <- 999
event_seed <- 999

mce_baseline_controls <- list(
  ECM_alpha = 0.2,
  X_trunc = TRUE,
  Xt_smooth = FALSE,
  smoother = NULL,
  CR_S0_shrink_diag = 0.4,
  CR_check_every = 10,
  CR_use_loglik = FALSE,
  CR_store_path = FALSE
)

mce_shock_controls <- list(
  reuse_ECM = TRUE,
  reuse_BS0 = TRUE,
  ECM_fallback = "baseline"
)

purchase_years <- 2011:2020
reporting_years <- purchase_years
N_members <- 1000
target_payout_per_member <- 100000
initial_position_per_member <- target_payout_per_member
initial_pool_cash <- N_members * initial_position_per_member
withdrawal_fraction <- 0.05
withdrawal_penalty_rate <- 0.005

q_full <- c(
  0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
  0.021506, 0.023614, 0.025473, 0.027789, 0.030319
)
stopifnot(length(q_full) >= length(purchase_years))
q <- q_full[seq_along(purchase_years)]

eta_params <- list(
  eta0 = 0.05,
  a = 1.25,
  b = 0.05,
  sigma = 0.05,
  substeps = 12
)

strategy_specs <- list(
  `5Y` = list(bond_maturity_years = 5),
  `10Y` = list(bond_maturity_years = 10)
)

baseline_model_names <- c("Observed", "DNS", "DLY", "MCE")
shock_model_names <- c("DNS", "DLY", "MCE")
```

```{r data}
yields <- tontine_read_yields(
  curve_files = curve_files,
  start_date = data_start_date,
  end_date = data_end_date
)
```

```{r valuation-windows}
valuation_windows <- tontine_build_valuation_windows(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = purchase_years,
  lookback_years = lookback_years,
  date_position = "first",
  valuation_date_position = "first"
)
```

```{r tontine-event-path}
member_pool <- tontine_create_member_pool(
  N_members = N_members,
  initial_position = initial_position_per_member
)

event_rung_schedule <- tontine_create_rung_schedule(
  purchase_years = purchase_years,
  bond_maturity_years = 1,
  contribution_per_member = 0,
  death_rates = q
)

eta_intensity_path <- tontine_simulate_cir_integrated_intensity(
  n_rungs = length(purchase_years),
  eta0 = eta_params$eta0,
  a = eta_params$a,
  b = eta_params$b,
  sigma = eta_params$sigma,
  substeps = eta_params$substeps,
  seed = event_seed
)

event_schedule <- tontine_create_event_schedule(
  purchase_years = purchase_years,
  death_rates = q,
  integrated_eta = eta_intensity_path$integrated_eta
)

event_path <- tontine_simulate_event_path(
  member_pool = member_pool,
  event_schedule = event_schedule,
  seed = event_seed
)

event_path %>%
  dplyr::select(
    rung_id, purchase_year, death_rate, death_count, survivors_after_death,
    integrated_eta, withdrawal_poisson_mean, raw_withdrawal_count,
    withdrawal_count, withdrawal_count_capped
  )
```

```{r baseline-models}
set.seed(fit_seed)

baseline_curve_models <- tontine_fit_rolling_baseline_curve_models(
  yields = yields,
  valuation_windows = valuation_windows,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  mce_controls = mce_baseline_controls,
  include_models = baseline_model_names,
  fit_seed = fit_seed
)
```

```{r multiyr-baseline-helpers}
build_multiyr_empty_holdings <- function() {
  data.frame(
    strategy = character(),
    model = character(),
    scenario = character(),
    scenario_type = character(),
    purchase_year = integer(),
    purchase_date = as.Date(character()),
    maturity_year = integer(),
    maturity_date = as.Date(character()),
    bond_maturity_years = integer(),
    country = character(),
    zero_rate = numeric(),
    purchase_cost = numeric(),
    maturity_proceeds = numeric(),
    bond_profit_loss = numeric(),
    stringsAsFactors = FALSE
  )
}

build_multiyr_empty_mtm <- function() {
  data.frame(
    strategy = character(),
    model = character(),
    scenario = character(),
    scenario_type = character(),
    valuation_year = integer(),
    valuation_date = as.Date(character()),
    purchase_year = integer(),
    purchase_date = as.Date(character()),
    maturity_year = integer(),
    maturity_date = as.Date(character()),
    remaining_maturity_years = numeric(),
    country = character(),
    purchase_cost = numeric(),
    maturity_proceeds = numeric(),
    mtm_zero_rate = numeric(),
    mtm_value = numeric(),
    mtm_profit_loss = numeric(),
    stringsAsFactors = FALSE
  )
}

build_multiyr_plot_y_limits <- function(values, symmetric = FALSE) {
  values <- values[is.finite(values)]
  if (length(values) == 0) {
    return(c(-1, 1))
  }

  if (isTRUE(symmetric)) {
    max_abs <- max(abs(values), 0)
    if (max_abs == 0) {
      max_abs <- 1
    }
    max_abs <- max_abs * 1.05
    return(c(-max_abs, max_abs))
  }

  value_range <- range(c(0, values))
  if (diff(value_range) == 0) {
    return(value_range + c(-1, 1))
  }

  value_range + c(-1, 1) * diff(value_range) * 0.05
}

multiyr_alive_position_total <- function(members) {
  sum(members$current_position[members$alive])
}

multiyr_scale_alive_positions_to_nav <- function(members, target_nav) {
  alive_idx <- which(members$alive)
  if (length(alive_idx) == 0) {
    return(members)
  }

  alive_position <- sum(members$current_position[alive_idx])
  if (alive_position <= 0) {
    members$current_position[alive_idx] <- target_nav / length(alive_idx)
    return(members)
  }

  members$current_position[alive_idx] <-
    members$current_position[alive_idx] * target_nav / alive_position
  members
}

multiyr_pool_book_nav <- function(cash_initial_reserve, cash_reinvestment, holdings) {
  cash_initial_reserve + cash_reinvestment + sum(holdings$purchase_cost)
}

multiyr_deduct_cash <- function(cash_initial_reserve, cash_reinvestment, amount) {
  amount <- as.numeric(amount)
  initial_draw <- min(cash_initial_reserve, amount)
  cash_initial_reserve <- cash_initial_reserve - initial_draw
  remaining <- amount - initial_draw
  reinvestment_draw <- min(cash_reinvestment, remaining)
  cash_reinvestment <- cash_reinvestment - reinvestment_draw
  liquidity_shortfall <- remaining - reinvestment_draw

  if (liquidity_shortfall > sqrt(.Machine$double.eps)) {
    cash_initial_reserve <- cash_initial_reserve - liquidity_shortfall
  }

  list(
    cash_initial_reserve = cash_initial_reserve,
    cash_reinvestment = cash_reinvestment,
    initial_draw = initial_draw,
    reinvestment_draw = reinvestment_draw,
    liquidity_shortfall = liquidity_shortfall
  )
}

multiyr_build_purchase_holdings <- function(model_obj, strategy_label,
                                            bond_maturity_years,
                                            purchase_year, purchase_date,
                                            investment_amount) {
  if (investment_amount <= 0) {
    return(build_multiyr_empty_holdings())
  }

  tenor_col <- tontine_bond_tenor_col(bond_maturity_years)
  if (!tenor_col %in% mat_names) {
    stop(sprintf("Missing required tenor `%s` for strategy `%s`.", tenor_col, strategy_label))
  }

  maturity_year <- purchase_year + bond_maturity_years
  maturity_date <- tontine_resolve_maturity_date(
    reference_panel = yields[[reference_curve]],
    purchase_date = purchase_date,
    maturity_year = maturity_year
  )
  country_purchase_cost <- investment_amount / length(curves)

  purrr::map_dfr(curves, function(country_name) {
    zero_rate <- tontine_extract_curve_rate(
      curve_panel = model_obj$curve_panels[[country_name]],
      target_date = purchase_date,
      tenor_col = tenor_col
    ) / 100
    country_maturity_proceeds <- country_purchase_cost * exp(zero_rate * bond_maturity_years)

    data.frame(
      strategy = strategy_label,
      model = model_obj$model,
      scenario = paste("Baseline", model_obj$model),
      scenario_type = "baseline",
      purchase_year = purchase_year,
      purchase_date = as.Date(purchase_date),
      maturity_year = maturity_year,
      maturity_date = as.Date(maturity_date),
      bond_maturity_years = bond_maturity_years,
      country = country_name,
      zero_rate = zero_rate,
      purchase_cost = country_purchase_cost,
      maturity_proceeds = country_maturity_proceeds,
      bond_profit_loss = country_maturity_proceeds - country_purchase_cost,
      stringsAsFactors = FALSE
    )
  })
}

multiyr_mark_to_market_holdings <- function(holdings, model_obj, valuation_year,
                                            valuation_date) {
  outstanding_holdings <- holdings[
    holdings$purchase_year <= valuation_year &
      as.Date(holdings$maturity_date) > as.Date(valuation_date),
    ,
    drop = FALSE
  ]
  if (nrow(outstanding_holdings) == 0) {
    return(build_multiyr_empty_mtm())
  }

  out <- outstanding_holdings
  out$valuation_year <- valuation_year
  out$valuation_date <- as.Date(valuation_date)
  out$remaining_maturity_years <-
    as.numeric(as.Date(out$maturity_date) - as.Date(valuation_date)) / 365.25
  out$remaining_maturity_years <- pmax(out$remaining_maturity_years, 1 / 365.25)
  out$mtm_zero_rate <- vapply(seq_len(nrow(out)), function(i) {
    interpolate_curve_rate(
      curve_panel = model_obj$curve_panels[[out$country[[i]]]],
      target_date = valuation_date,
      target_months = 12 * out$remaining_maturity_years[[i]],
      mats = mats,
      mat_names = mat_names,
      rate_scale = "decimal"
    )
  }, numeric(1))
  out$mtm_value <-
    out$maturity_proceeds * exp(-out$mtm_zero_rate * out$remaining_maturity_years)
  out$mtm_profit_loss <- out$mtm_value - out$purchase_cost

  out[, c(
    "strategy", "model", "scenario", "scenario_type",
    "valuation_year", "valuation_date", "purchase_year", "purchase_date",
    "maturity_year", "maturity_date", "remaining_maturity_years",
    "country", "purchase_cost", "maturity_proceeds",
    "mtm_zero_rate", "mtm_value", "mtm_profit_loss"
  )]
}

simulate_multiyr_baseline_strategy <- function(model_obj, strategy_label,
                                               bond_maturity_years) {
  members <- member_pool
  cash_initial_reserve <- initial_pool_cash
  cash_reinvestment <- 0
  holdings <- build_multiyr_empty_holdings()
  all_holdings <- build_multiyr_empty_holdings()
  realized_country_rows <- list()
  mtm_country_rows <- list()
  history_rows <- vector("list", length(purchase_years))
  state <- tontine_initialize_state(
    member_pool = members,
    withdrawal_settings = tontine_withdrawal_settings(
      withdrawal_fraction = withdrawal_fraction,
      withdrawal_penalty_rate = withdrawal_penalty_rate
    )
  )

  for (i in seq_along(purchase_years)) {
    purchase_year <- purchase_years[[i]]
    purchase_date <- valuation_windows$purchase_date[[i]]
    valuation_date <- valuation_windows$valuation_date[[i]]
    event_row <- event_path[event_path$rung_id == i, , drop = FALSE]
    if (nrow(event_row) != 1) {
      stop("`event_path` must contain exactly one row per purchase year.")
    }

    active_start_count <- sum(members$alive)
    book_nav_start <- multiyr_pool_book_nav(
      cash_initial_reserve = cash_initial_reserve,
      cash_reinvestment = cash_reinvestment,
      holdings = holdings
    )
    members <- multiyr_scale_alive_positions_to_nav(members, book_nav_start)
    active_position_start <- multiyr_alive_position_total(members)

    maturing_holdings <- holdings[
      as.Date(holdings$maturity_date) <= as.Date(purchase_date),
      ,
      drop = FALSE
    ]
    maturity_proceeds <- sum(maturing_holdings$maturity_proceeds)
    maturity_book_cost <- sum(maturing_holdings$purchase_cost)
    realized_bond_profit_loss <- sum(maturing_holdings$bond_profit_loss)
    if (nrow(maturing_holdings) > 0) {
      realized_country_rows[[length(realized_country_rows) + 1]] <- maturing_holdings %>%
        dplyr::mutate(realization_year = purchase_year)
      holdings <- holdings[
        !(as.Date(holdings$maturity_date) <= as.Date(purchase_date)),
        ,
        drop = FALSE
      ]
      cash_reinvestment <- cash_reinvestment + maturity_proceeds
      members <- multiyr_scale_alive_positions_to_nav(
        members,
        multiyr_pool_book_nav(cash_initial_reserve, cash_reinvestment, holdings)
      )
    }

    state$members <- members
    death_result <- tontine_apply_deaths(
      state = state,
      rung_id = i,
      death_member_ids = event_row$death_member_ids[[1]]
    )
    members <- death_result$state$members
    members <- multiyr_scale_alive_positions_to_nav(
      members,
      multiyr_pool_book_nav(cash_initial_reserve, cash_reinvestment, holdings)
    )

    state$members <- members
    withdrawal_result <- tontine_apply_withdrawals(
      state = state,
      rung_id = i,
      withdrawal_member_ids = event_row$withdrawal_member_ids[[1]]
    )
    members <- withdrawal_result$state$members
    cash_after_withdrawal <- multiyr_deduct_cash(
      cash_initial_reserve = cash_initial_reserve,
      cash_reinvestment = cash_reinvestment,
      amount = withdrawal_result$total_withdrawal
    )
    cash_initial_reserve <- cash_after_withdrawal$cash_initial_reserve
    cash_reinvestment <- cash_after_withdrawal$cash_reinvestment
    members <- multiyr_scale_alive_positions_to_nav(
      members,
      multiyr_pool_book_nav(cash_initial_reserve, cash_reinvestment, holdings)
    )

    remaining_seed_years <- max(bond_maturity_years - i + 1L, 0L)
    scheduled_initial_investment <- if (remaining_seed_years > 0) {
      max(cash_initial_reserve, 0) / remaining_seed_years
    } else {
      0
    }
    reinvestment_investment <- max(cash_reinvestment, 0)
    total_investment <- scheduled_initial_investment + reinvestment_investment

    new_holdings <- multiyr_build_purchase_holdings(
      model_obj = model_obj,
      strategy_label = strategy_label,
      bond_maturity_years = bond_maturity_years,
      purchase_year = purchase_year,
      purchase_date = purchase_date,
      investment_amount = total_investment
    )
    if (nrow(new_holdings) > 0) {
      holdings <- rbind(holdings, new_holdings)
      all_holdings <- rbind(all_holdings, new_holdings)
    }
    cash_initial_reserve <- cash_initial_reserve - scheduled_initial_investment
    cash_reinvestment <- cash_reinvestment - reinvestment_investment

    book_nav_end <- multiyr_pool_book_nav(
      cash_initial_reserve = cash_initial_reserve,
      cash_reinvestment = cash_reinvestment,
      holdings = holdings
    )
    mtm_holdings <- multiyr_mark_to_market_holdings(
      holdings = holdings,
      model_obj = model_obj,
      valuation_year = purchase_year,
      valuation_date = valuation_date
    )
    outstanding_bond_mtm_value <- sum(mtm_holdings$mtm_value)
    outstanding_bond_mtm_profit_loss <- sum(mtm_holdings$mtm_profit_loss)
    mtm_nav_end <- cash_initial_reserve + cash_reinvestment + outstanding_bond_mtm_value
    if (nrow(mtm_holdings) > 0) {
      mtm_country_rows[[length(mtm_country_rows) + 1]] <- mtm_holdings
    }

    members <- multiyr_scale_alive_positions_to_nav(members, book_nav_end)
    active_end_count <- sum(members$alive)
    active_position_end <- multiyr_alive_position_total(members)

    history_rows[[i]] <- data.frame(
      strategy = strategy_label,
      model = model_obj$model,
      scenario = paste("Baseline", model_obj$model),
      scenario_type = "baseline",
      rung_id = i,
      purchase_year = purchase_year,
      purchase_date = as.Date(purchase_date),
      valuation_date = as.Date(valuation_date),
      bond_maturity_years = bond_maturity_years,
      active_start_count = active_start_count,
      active_position_start = active_position_start,
      death_count = length(event_row$death_member_ids[[1]]),
      death_forfeited_position = death_result$forfeited_position,
      active_after_deaths_count = sum(members$alive),
      integrated_eta = event_row$integrated_eta[[1]],
      withdrawal_poisson_mean = event_row$withdrawal_poisson_mean[[1]],
      raw_withdrawal_count = event_row$raw_withdrawal_count[[1]],
      withdrawal_count = length(event_row$withdrawal_member_ids[[1]]),
      withdrawal_count_capped = event_row$withdrawal_count_capped[[1]],
      total_withdrawal = withdrawal_result$total_withdrawal,
      withdrawal_penalty = withdrawal_result$total_penalty,
      withdrawal_liquidity_shortfall = cash_after_withdrawal$liquidity_shortfall,
      maturity_book_cost = maturity_book_cost,
      maturity_proceeds = maturity_proceeds,
      realized_bond_profit_loss = realized_bond_profit_loss,
      scheduled_initial_investment = scheduled_initial_investment,
      reinvestment_investment = reinvestment_investment,
      total_purchase_cost = total_investment,
      cash_initial_reserve_end = cash_initial_reserve,
      cash_reinvestment_end = cash_reinvestment,
      cash_total_end = cash_initial_reserve + cash_reinvestment,
      outstanding_bond_book_value = sum(holdings$purchase_cost),
      outstanding_bond_mtm_value = outstanding_bond_mtm_value,
      outstanding_bond_mtm_profit_loss = outstanding_bond_mtm_profit_loss,
      book_nav_end = book_nav_end,
      mtm_nav_end = mtm_nav_end,
      active_end_count = active_end_count,
      active_position_end = active_position_end,
      average_book_position_end =
        ifelse(active_end_count > 0, active_position_end / active_end_count, NA_real_),
      average_mtm_position_end =
        ifelse(active_end_count > 0, mtm_nav_end / active_end_count, NA_real_),
      stringsAsFactors = FALSE
    )

    state$members <- members
  }

  list(
    rung_history = dplyr::bind_rows(history_rows),
    holdings_outstanding = holdings,
    holdings_all = all_holdings,
    realized_country_pl = dplyr::bind_rows(realized_country_rows),
    country_mtm = dplyr::bind_rows(mtm_country_rows)
  )
}
```

```{r baseline-valuations}
baseline_strategy_replays <- purrr::imap(strategy_specs, function(strategy_spec, strategy_label) {
  purrr::imap(baseline_curve_models, function(model_obj, model_key) {
    simulate_multiyr_baseline_strategy(
      model_obj = model_obj,
      strategy_label = strategy_label,
      bond_maturity_years = strategy_spec$bond_maturity_years
    )
  })
})

baseline_rung_summary <- dplyr::bind_rows(unlist(
  purrr::map(baseline_strategy_replays, function(strategy_replays) {
    purrr::map(strategy_replays, "rung_history")
  }),
  recursive = FALSE
))

baseline_holdings_outstanding <- dplyr::bind_rows(unlist(
  purrr::map(baseline_strategy_replays, function(strategy_replays) {
    purrr::map(strategy_replays, "holdings_outstanding")
  }),
  recursive = FALSE
))

baseline_holdings_all <- dplyr::bind_rows(unlist(
  purrr::map(baseline_strategy_replays, function(strategy_replays) {
    purrr::map(strategy_replays, "holdings_all")
  }),
  recursive = FALSE
))

baseline_realized_country_pl <- dplyr::bind_rows(unlist(
  purrr::map(baseline_strategy_replays, function(strategy_replays) {
    purrr::map(strategy_replays, "realized_country_pl")
  }),
  recursive = FALSE
))

baseline_country_mtm <- dplyr::bind_rows(unlist(
  purrr::map(baseline_strategy_replays, function(strategy_replays) {
    purrr::map(strategy_replays, "country_mtm")
  }),
  recursive = FALSE
))
```

```{r baseline-summaries}
baseline_model_summary <- baseline_rung_summary %>%
  dplyr::group_by(strategy, model) %>%
  dplyr::summarise(
    final_active_members = dplyr::last(active_end_count),
    final_book_nav = dplyr::last(book_nav_end),
    final_mtm_nav = dplyr::last(mtm_nav_end),
    final_average_book_position = dplyr::last(average_book_position_end),
    final_average_mtm_position = dplyr::last(average_mtm_position_end),
    final_cash_total = dplyr::last(cash_total_end),
    final_cash_initial_reserve = dplyr::last(cash_initial_reserve_end),
    final_cash_reinvestment = dplyr::last(cash_reinvestment_end),
    final_outstanding_bond_book_value = dplyr::last(outstanding_bond_book_value),
    final_outstanding_bond_mtm_value = dplyr::last(outstanding_bond_mtm_value),
    total_withdrawals = sum(total_withdrawal),
    total_withdrawal_penalties = sum(withdrawal_penalty),
    total_withdrawal_liquidity_shortfall = sum(withdrawal_liquidity_shortfall),
    total_maturity_proceeds = sum(maturity_proceeds),
    total_realized_bond_profit_loss = sum(realized_bond_profit_loss),
    .groups = "drop"
  ) %>%
  dplyr::arrange(strategy, model)

baseline_cash_summary <- baseline_rung_summary %>%
  dplyr::select(
    strategy, model, purchase_year, cash_initial_reserve_end,
    cash_reinvestment_end, cash_total_end, withdrawal_liquidity_shortfall,
    scheduled_initial_investment, reinvestment_investment
  ) %>%
  dplyr::arrange(strategy, purchase_year, model)

baseline_realized_country_pl_summary <- baseline_realized_country_pl %>%
  dplyr::group_by(strategy, model, country) %>%
  dplyr::summarise(
    realized_purchase_cost = sum(purchase_cost),
    realized_maturity_proceeds = sum(maturity_proceeds),
    realized_bond_profit_loss = sum(bond_profit_loss),
    .groups = "drop"
  ) %>%
  dplyr::mutate(country = toupper(country)) %>%
  dplyr::arrange(strategy, country, model)

baseline_country_mtm_summary <- baseline_country_mtm %>%
  dplyr::group_by(strategy, model, valuation_year, valuation_date, country) %>%
  dplyr::summarise(
    outstanding_purchase_cost = sum(purchase_cost),
    outstanding_maturity_proceeds = sum(maturity_proceeds),
    mtm_value = sum(mtm_value),
    mtm_profit_loss = sum(mtm_profit_loss),
    active_holding_count = dplyr::n_distinct(purchase_year),
    .groups = "drop"
  ) %>%
  dplyr::mutate(country = toupper(country)) %>%
  dplyr::arrange(strategy, valuation_year, country, model)

baseline_total_mtm_summary <- baseline_country_mtm_summary %>%
  dplyr::group_by(strategy, model, valuation_year, valuation_date) %>%
  dplyr::summarise(
    outstanding_purchase_cost = sum(outstanding_purchase_cost),
    outstanding_maturity_proceeds = sum(outstanding_maturity_proceeds),
    mtm_value = sum(mtm_value),
    mtm_profit_loss = sum(mtm_profit_loss),
    active_holding_count = sum(active_holding_count),
    .groups = "drop"
  ) %>%
  dplyr::left_join(
    baseline_rung_summary %>%
      dplyr::select(
        strategy, model,
        valuation_year = purchase_year,
        cash_initial_reserve_end,
        cash_reinvestment_end,
        cash_total_end,
        mtm_nav_end,
        average_mtm_position_end
      ),
    by = c("strategy", "model", "valuation_year")
  ) %>%
  dplyr::arrange(strategy, valuation_year, model)

baseline_rung_summary
baseline_model_summary
baseline_cash_summary
baseline_realized_country_pl_summary
baseline_country_mtm_summary
baseline_total_mtm_summary
```

## MTM Shock Examples

These shocks revalue baseline holdings only. The mortality path, withdrawal
path, purchases, maturity proceeds, and reinvestment schedule remain fixed.

```{r shock-specs}
shock_ramp_start_fraction <- 0.30 / length(2015:2020)

shock_examples <- list(
  global_l_pos30pct_decay_2015_2020 = list(
    label = "Global L +30% average level linear decay 2015-2020",
    shock_profile = "linear_decay",
    shock_start_year = 2015,
    shock_start_anchor = "valuation_date",
    shock_end_year = 2020,
    shock_end_anchor = "valuation_date",
    shock_effect_timing = "full_window",
    shock_curves = curves,
    shock_factors = "L",
    shock_start_magnitude = 0.30,
    shock_end_magnitude = 0.0,
    shock_basis = "average_level_fraction",
    shock_type = "additive"
  ),
  global_l_pos30pct_increase_2015_2020 = list(
    label = "Global L increasing positive average level shock 2015-2020",
    shock_profile = "linear_increase",
    shock_start_year = 2015,
    shock_start_anchor = "valuation_date",
    shock_end_year = 2020,
    shock_end_anchor = "valuation_date",
    shock_effect_timing = "full_window",
    shock_curves = curves,
    shock_factors = "L",
    shock_start_magnitude = shock_ramp_start_fraction,
    shock_end_magnitude = 0.30,
    shock_basis = "average_level_fraction",
    shock_type = "additive"
  )
)
```

```{r shock-models}
shock_curve_models <- purrr::imap(shock_examples, function(shock_spec, shock_key) {
  tontine_fit_rolling_shocked_curve_models(
    yields = yields,
    valuation_windows = valuation_windows,
    curves = curves,
    mats = mats,
    mat_names = mat_names,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference_curve = reference_curve,
    shock_spec = shock_spec,
    mce_controls = mce_baseline_controls,
    mce_shock_controls = mce_shock_controls,
    include_models = shock_model_names,
    fit_seed = fit_seed
  )
})
```

```{r shock-mtm-valuations}
multiyr_mark_baseline_holdings_to_curve_models <- function(holdings, curve_models,
                                                           shock_key, shock_label) {
  purrr::imap_dfr(curve_models, function(model_obj, model_key) {
    model_holdings <- holdings %>%
      dplyr::filter(.data$model == model_obj$model)

    purrr::map_dfr(seq_len(nrow(valuation_windows)), function(i) {
      multiyr_mark_to_market_holdings(
        holdings = model_holdings,
        model_obj = model_obj,
        valuation_year = valuation_windows$purchase_year[[i]],
        valuation_date = valuation_windows$valuation_date[[i]]
      ) %>%
        dplyr::mutate(
          shock_key = .env$shock_key,
          shock_label = .env$shock_label
        )
    })
  })
}

shock_country_mtm <- purrr::imap_dfr(shock_curve_models, function(curve_models, shock_key) {
  multiyr_mark_baseline_holdings_to_curve_models(
    holdings = baseline_holdings_all,
    curve_models = curve_models,
    shock_key = shock_key,
    shock_label = shock_examples[[shock_key]]$label
  )
})

shock_country_mtm_summary <- shock_country_mtm %>%
  dplyr::group_by(
    shock_key, shock_label, strategy, model,
    valuation_year, valuation_date, country
  ) %>%
  dplyr::summarise(
    shocked_mtm_value = sum(mtm_value),
    shocked_mtm_profit_loss = sum(mtm_profit_loss),
    active_holding_count = dplyr::n_distinct(purchase_year),
    .groups = "drop"
  ) %>%
  dplyr::mutate(country = toupper(.data$country)) %>%
  dplyr::left_join(
    baseline_country_mtm_summary %>%
      dplyr::filter(.data$model %in% shock_model_names) %>%
      dplyr::select(
        strategy, model, valuation_year, country,
        baseline_mtm_value = mtm_value,
        baseline_mtm_profit_loss = mtm_profit_loss
      ),
    by = c("strategy", "model", "valuation_year", "country")
  ) %>%
  dplyr::mutate(
    mtm_value_delta = .data$shocked_mtm_value - .data$baseline_mtm_value,
    mtm_profit_loss_delta =
      .data$shocked_mtm_profit_loss - .data$baseline_mtm_profit_loss
  ) %>%
  dplyr::arrange(shock_label, strategy, valuation_year, country, model)

shock_country_mtm_summary
```

## Visualizations

```{r visualization-data}
model_levels <- c("Observed", "DNS", "DLY", "MCE")
model_palette <- c(
  Observed = "#7E6A9E",
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)
year_breaks <- reporting_years
shock_model_palette <- model_palette[shock_model_names]
shock_scenario_labels <- vapply(shock_examples, `[[`, character(1), "label")

format_multiyr_shock_label <- function(scenario_label) {
  if (identical(scenario_label, "Global L +30% average level linear decay 2015-2020")) {
    "+30% Global L Decay Shock"
  } else if (identical(scenario_label, "Global L increasing positive average level shock 2015-2020")) {
    "+30% Global L Increase Shock"
  } else {
    scenario_label
  }
}

baseline_plot_data <- baseline_rung_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

baseline_total_mtm_plot_data <- baseline_total_mtm_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

baseline_country_mtm_plot_data <- baseline_country_mtm_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

shock_country_mtm_plot_data <- shock_country_mtm_summary %>%
  dplyr::mutate(
    model = factor(model, levels = shock_model_names),
    shock_label = factor(.data$shock_label, levels = shock_scenario_labels)
  )

average_mtm_position_y_limits <- build_multiyr_plot_y_limits(
  baseline_plot_data$average_mtm_position_end
)
mtm_nav_y_limits <- build_multiyr_plot_y_limits(
  baseline_total_mtm_plot_data$mtm_nav_end
)
country_mtm_value_y_limits <- build_multiyr_plot_y_limits(
  baseline_country_mtm_plot_data$mtm_value
)
country_mtm_pl_y_limits <- build_multiyr_plot_y_limits(
  baseline_country_mtm_plot_data$mtm_profit_loss,
  symmetric = TRUE
)
shock_country_mtm_pl_delta_y_limits <- build_multiyr_plot_y_limits(
  shock_country_mtm_plot_data$mtm_profit_loss_delta,
  symmetric = TRUE
)
shock_country_mtm_pl_delta_non_usa_y_limits <- build_multiyr_plot_y_limits(
  shock_country_mtm_plot_data %>%
    dplyr::filter(.data$country != "USA") %>%
    dplyr::pull(.data$mtm_profit_loss_delta),
  symmetric = TRUE
)

build_multiyr_average_mtm_position_plot <- function(plot_data, strategy_label) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$strategy == strategy_label),
    ggplot2::aes(x = purchase_year, y = average_mtm_position_end, color = model)
  ) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format(), limits = average_mtm_position_y_limits) +
    ggplot2::labs(
      title = paste("Baseline Average Survivor MTM Wealth:", strategy_label),
      x = "Valuation Year",
      y = "Average Survivor MTM Wealth",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_mtm_nav_plot <- function(plot_data, strategy_label) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$strategy == strategy_label),
    ggplot2::aes(x = valuation_year, y = mtm_nav_end, color = model)
  ) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format(), limits = mtm_nav_y_limits) +
    ggplot2::labs(
      title = paste("Baseline MTM Portfolio Value:", strategy_label),
      x = "Valuation Year",
      y = "MTM Portfolio Value",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_country_mtm_value_plot <- function(plot_data, strategy_label, country_name) {
  country_label <- toupper(country_name)

  ggplot2::ggplot(
    plot_data %>%
      dplyr::filter(
        .data$strategy == strategy_label,
        .data$country == country_label
      ),
    ggplot2::aes(x = valuation_year, y = mtm_value, color = model)
  ) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format(), limits = country_mtm_value_y_limits) +
    ggplot2::labs(
      title = paste("Baseline Country MTM Bond Value:", strategy_label, country_label),
      x = "Valuation Year",
      y = "Country MTM Bond Value",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_country_mtm_pl_plot <- function(plot_data, strategy_label, country_name) {
  country_label <- toupper(country_name)

  ggplot2::ggplot(
    plot_data %>%
      dplyr::filter(
        .data$strategy == strategy_label,
        .data$country == country_label
      ),
    ggplot2::aes(x = valuation_year, y = mtm_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format(), limits = country_mtm_pl_y_limits) +
    ggplot2::labs(
      title = paste("Baseline Country MTM P/L:", strategy_label, country_label),
      x = "Valuation Year",
      y = "Country MTM P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

country_mtm_value_plots <- setNames(lapply(names(strategy_specs), function(strategy_label) {
  setNames(lapply(curves, function(country_name) {
    build_multiyr_country_mtm_value_plot(
      baseline_country_mtm_plot_data,
      strategy_label,
      country_name
    )
  }), curves)
}), names(strategy_specs))

country_mtm_plots <- setNames(lapply(names(strategy_specs), function(strategy_label) {
  setNames(lapply(curves, function(country_name) {
    build_multiyr_country_mtm_pl_plot(
      baseline_country_mtm_plot_data,
      strategy_label,
      country_name
    )
  }), curves)
}), names(strategy_specs))

build_multiyr_country_shock_mtm_pl_delta_plot <- function(plot_data, strategy_label,
                                                          country_name, scenario_label) {
  country_label <- toupper(country_name)
  y_limits <- if (country_label == "USA") {
    shock_country_mtm_pl_delta_y_limits
  } else {
    shock_country_mtm_pl_delta_non_usa_y_limits
  }

  ggplot2::ggplot(
    plot_data %>%
      dplyr::filter(
        .data$strategy == strategy_label,
        .data$country == country_label,
        .data$shock_label == scenario_label
      ),
    ggplot2::aes(x = valuation_year, y = mtm_profit_loss_delta, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
    ggplot2::scale_y_continuous(
      labels = scales::dollar_format(),
      limits = y_limits
    ) +
    ggplot2::labs(
      title = paste(
        "Shock Country MTM P/L Delta:",
        strategy_label,
        country_label,
        format_multiyr_shock_label(as.character(scenario_label))
      ),
      x = "Valuation Year",
      y = "Change in Country MTM P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

country_shock_mtm_pl_delta_plots <- purrr::imap(shock_scenario_labels, function(scenario_label, shock_key) {
  setNames(lapply(names(strategy_specs), function(strategy_label) {
    setNames(lapply(curves, function(country_name) {
      build_multiyr_country_shock_mtm_pl_delta_plot(
        shock_country_mtm_plot_data,
        strategy_label,
        country_name,
        scenario_label
      )
    }), curves)
  }), names(strategy_specs))
})
```

```{r plot-average-survivor-wealth-5y}
build_multiyr_average_mtm_position_plot(baseline_plot_data, "5Y")
```

```{r plot-average-survivor-wealth-10y}
build_multiyr_average_mtm_position_plot(baseline_plot_data, "10Y")
```

```{r plot-mtm-portfolio-value-5y}
build_multiyr_mtm_nav_plot(baseline_total_mtm_plot_data, "5Y")
```

```{r plot-mtm-portfolio-value-10y}
build_multiyr_mtm_nav_plot(baseline_total_mtm_plot_data, "10Y")
```

```{r plot-country-mtm-value-5y-usa}
country_mtm_value_plots$`5Y`$usa
```

```{r plot-country-mtm-value-5y-gbr}
country_mtm_value_plots$`5Y`$gbr
```

```{r plot-country-mtm-value-5y-jpn}
country_mtm_value_plots$`5Y`$jpn
```

```{r plot-country-mtm-value-5y-ger}
country_mtm_value_plots$`5Y`$ger
```

```{r plot-country-mtm-value-10y-usa}
country_mtm_value_plots$`10Y`$usa
```

```{r plot-country-mtm-value-10y-gbr}
country_mtm_value_plots$`10Y`$gbr
```

```{r plot-country-mtm-value-10y-jpn}
country_mtm_value_plots$`10Y`$jpn
```

```{r plot-country-mtm-value-10y-ger}
country_mtm_value_plots$`10Y`$ger
```

```{r plot-country-mtm-pl-5y-usa}
country_mtm_plots$`5Y`$usa

```

```{r plot-country-mtm-pl-5y-gbr}
country_mtm_plots$`5Y`$gbr
```

```{r plot-country-mtm-pl-5y-jpn}
country_mtm_plots$`5Y`$jpn
```

```{r plot-country-mtm-pl-5y-ger}
country_mtm_plots$`5Y`$ger
```

```{r plot-country-mtm-pl-10y-usa}
country_mtm_plots$`10Y`$usa
```

```{r plot-country-mtm-pl-10y-gbr}
country_mtm_plots$`10Y`$gbr
```

```{r plot-country-mtm-pl-10y-jpn}
country_mtm_plots$`10Y`$jpn
```

```{r plot-country-mtm-pl-10y-ger}
country_mtm_plots$`10Y`$ger
```

```{r plot-shock-country-mtm-pl-delta-decay-5y-usa}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`5Y`$usa
```

```{r plot-shock-country-mtm-pl-delta-decay-5y-gbr}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`5Y`$gbr
```

```{r plot-shock-country-mtm-pl-delta-decay-5y-jpn}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`5Y`$jpn
```

```{r plot-shock-country-mtm-pl-delta-decay-5y-ger}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`5Y`$ger
```

```{r plot-shock-country-mtm-pl-delta-decay-10y-usa}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`10Y`$usa
```

```{r plot-shock-country-mtm-pl-delta-decay-10y-gbr}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`10Y`$gbr
```

```{r plot-shock-country-mtm-pl-delta-decay-10y-jpn}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`10Y`$jpn
```

```{r plot-shock-country-mtm-pl-delta-decay-10y-ger}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_decay_2015_2020$`10Y`$ger
```

```{r plot-shock-country-mtm-pl-delta-increase-5y-usa}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`5Y`$usa
```

```{r plot-shock-country-mtm-pl-delta-increase-5y-gbr}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`5Y`$gbr
```

```{r plot-shock-country-mtm-pl-delta-increase-5y-jpn}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`5Y`$jpn
```

```{r plot-shock-country-mtm-pl-delta-increase-5y-ger}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`5Y`$ger
```

```{r plot-shock-country-mtm-pl-delta-increase-10y-usa}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`10Y`$usa
```

```{r plot-shock-country-mtm-pl-delta-increase-10y-gbr}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`10Y`$gbr
```

```{r plot-shock-country-mtm-pl-delta-increase-10y-jpn}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`10Y`$jpn
```

```{r plot-shock-country-mtm-pl-delta-increase-10y-ger}
country_shock_mtm_pl_delta_plots$global_l_pos30pct_increase_2015_2020$`10Y`$ger
```


```{r}
baseline_country_mtm_plot_data %>% filter(strategy == '5Y' & valuation_year == 2018 & country == 'USA')
```
