---
title: "Tontine Stress Test: 1-Year Reinvestment Pool"
date: "2026-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Purpose

This notebook evaluates a closed 1-year tontine reinvestment pool. Members
start with an initial position, deaths and partial withdrawals occur each rung,
and surviving member positions fund the next 1-year bond purchase. Bond
proceeds, mortality redistribution, and deferred withdrawal penalties are fully
reinvested into surviving members' next-rung positions.

```{r libraries}
library(here)
library(dplyr)
library(purrr)
library(ggplot2)
library(scales)
library(tibble)
library(vars)
library(tsDyn)
library(Matrix)

sys.source(here::here("applications", "tontine_helpers.R"), envir = .GlobalEnv)
sys.source(here::here("applications", "tontine_setup.R"), envir = .GlobalEnv)
tontine_source_project()
```

```{r configuration}
curve_files <- list(
  usa = "usa-bs.csv",
  gbr = "gbr-bs.csv",
  jpn = "jpn-bs.csv",
  ger = "ger-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "usa"

mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- tontine_mat_names(mats)
one_year_tenor <- tontine_bond_tenor_col(1)

data_start_date <- as.Date("2010-01-01")
data_end_date <- as.Date("2021-12-31")
lookback_years <- 1

lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)
fit_seed <- 999
event_seed <- 20260430

mce_baseline_controls <- list(
  ECM_alpha = 0.2,
  X_trunc = TRUE,
  Xt_smooth = FALSE,
  smoother = NULL,
  CR_S0_shrink_diag = 0.4,
  CR_check_every = 10,
  CR_use_loglik = FALSE,
  CR_store_path = FALSE
)

mce_shock_controls <- list(
  reuse_ECM = TRUE,
  reuse_BS0 = TRUE,
  ECM_fallback = "baseline"
)

purchase_years <- 2011:2020
N_members <- 1000
target_payout_per_member <- 100000
initial_position_per_member <- target_payout_per_member
withdrawal_fraction <- 0.05
withdrawal_penalty_rate <- 0.005

q_full <- c(
  0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
  0.021506, 0.023614, 0.025473, 0.027789, 0.030319
)
stopifnot(length(q_full) >= length(purchase_years))
q <- q_full[seq_along(purchase_years)]

eta_params <- list(
  eta0 = 0.05,
  a = 1.25,
  b = 0.05,
  sigma = 0.05,
  substeps = 12
)

baseline_model_names <- c("Observed", "DNS", "DLY", "MCE")
shock_model_names <- c("DNS", "DLY", "MCE")
```

```{r data}
yields <- tontine_read_yields(
  curve_files = curve_files,
  start_date = data_start_date,
  end_date = data_end_date
)
```

```{r valuation-windows}
valuation_windows <- tontine_build_valuation_windows(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = purchase_years,
  lookback_years = lookback_years
)
```

```{r tontine-event-path}
member_pool <- tontine_create_member_pool(
  N_members = N_members,
  initial_position = initial_position_per_member
)

rung_schedule <- tontine_create_rung_schedule(
  purchase_years = purchase_years,
  bond_maturity_years = 1,
  contribution_per_member = 0,
  death_rates = q
)

eta_intensity_path <- tontine_simulate_cir_integrated_intensity(
  n_rungs = length(purchase_years),
  eta0 = eta_params$eta0,
  a = eta_params$a,
  b = eta_params$b,
  sigma = eta_params$sigma,
  substeps = eta_params$substeps,
  seed = event_seed
)

event_schedule <- tontine_create_event_schedule(
  purchase_years = purchase_years,
  death_rates = q,
  integrated_eta = eta_intensity_path$integrated_eta
)

event_path <- tontine_simulate_event_path(
  member_pool = member_pool,
  event_schedule = event_schedule,
  seed = event_seed
)

event_path %>%
  dplyr::select(
    rung_id, purchase_year, death_rate, death_count, survivors_after_death,
    integrated_eta, withdrawal_poisson_mean, raw_withdrawal_count,
    withdrawal_count, withdrawal_count_capped
  )
```

```{r baseline-models}
set.seed(fit_seed)

baseline_curve_models <- tontine_fit_rolling_baseline_curve_models(
  yields = yields,
  valuation_windows = valuation_windows,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  mce_controls = mce_baseline_controls,
  include_models = baseline_model_names,
  fit_seed = fit_seed
)
```

```{r return-factor-helpers}
build_1yr_return_factors <- function(curve_models, scenario_type, scenario_name_prefix,
                                     shock_label = NA_character_) {
  purrr::imap_dfr(curve_models, function(model_obj, model_key) {
    purrr::map_dfr(seq_len(nrow(valuation_windows)), function(i) {
      purchase_date <- valuation_windows$purchase_date[[i]]
      zero_rates <- vapply(curves, function(country_name) {
        tontine_extract_curve_rate(
          curve_panel = model_obj$curve_panels[[country_name]],
          target_date = purchase_date,
          tenor_col = one_year_tenor
        ) / 100
      }, numeric(1))

      discount_factors <- exp(-zero_rates)

      tibble::tibble(
        model = model_obj$model,
        scenario = paste(scenario_name_prefix, model_obj$model),
        scenario_type = scenario_type,
        shock_label = shock_label,
        rung_id = valuation_windows$rung_id[[i]],
        purchase_year = valuation_windows$purchase_year[[i]],
        purchase_date = purchase_date,
        average_1y_zero_rate = mean(zero_rates),
        gross_return_factor = mean(1 / discount_factors)
      )
    })
  })
}

build_1yr_country_return_factors <- function(curve_models, scenario_type, scenario_name_prefix,
                                             shock_label = NA_character_) {
  purrr::imap_dfr(curve_models, function(model_obj, model_key) {
    purrr::map_dfr(seq_len(nrow(valuation_windows)), function(i) {
      purchase_date <- valuation_windows$purchase_date[[i]]

      purrr::map_dfr(curves, function(country_name) {
        zero_rate <- tontine_extract_curve_rate(
          curve_panel = model_obj$curve_panels[[country_name]],
          target_date = purchase_date,
          tenor_col = one_year_tenor
        ) / 100

        tibble::tibble(
          model = model_obj$model,
          scenario = paste(scenario_name_prefix, model_obj$model),
          scenario_type = scenario_type,
          shock_label = shock_label,
          rung_id = valuation_windows$rung_id[[i]],
          purchase_year = valuation_windows$purchase_year[[i]],
          purchase_date = purchase_date,
          country = country_name,
          country_1y_zero_rate = zero_rate,
          country_gross_return_factor = exp(zero_rate)
        )
      })
    })
  })
}

build_1yr_country_bond_pl <- function(rung_summary, country_return_factors) {
  rung_summary %>%
    dplyr::left_join(
      country_return_factors,
      by = c("model", "scenario", "scenario_type", "shock_label", "rung_id", "purchase_year")
    ) %>%
    dplyr::mutate(
      country_purchase_cost = .data$investable_position / length(curves),
      country_maturity_proceeds = .data$country_purchase_cost * .data$country_gross_return_factor,
      country_bond_profit_loss = .data$country_maturity_proceeds - .data$country_purchase_cost
    )
}

replay_1yr_return_factors <- function(return_factors) {
  model_states <- lapply(split(return_factors, return_factors$model), function(model_return_factors) {
    model_return_factors <- model_return_factors %>%
      dplyr::arrange(.data$rung_id)

    tontine_replay_1yr_reinvestment_path(
      member_pool = member_pool,
      rung_schedule = rung_schedule,
      event_path = event_path,
      gross_return_factors = model_return_factors,
      withdrawal_settings = tontine_withdrawal_settings(
        withdrawal_fraction = withdrawal_fraction,
        withdrawal_penalty_rate = withdrawal_penalty_rate
      ),
      payout_settings = tontine_payout_settings(
        allocation = "position_weighted",
        penalty_timing = "next_rung",
        position_update = "replace_with_payout"
      ),
      model = unique(model_return_factors$model),
      scenario = unique(model_return_factors$scenario),
      scenario_type = unique(model_return_factors$scenario_type),
      shock_label = unique(model_return_factors$shock_label)
    )
  })

  list(
    states = model_states,
    rung_history = dplyr::bind_rows(lapply(model_states, `[[`, "rung_history")),
    member_events = dplyr::bind_rows(lapply(model_states, `[[`, "member_events"))
  )
}
```

```{r baseline-valuation}
baseline_return_factors <- build_1yr_return_factors(
  curve_models = baseline_curve_models,
  scenario_type = "baseline",
  scenario_name_prefix = "Baseline"
)

baseline_country_return_factors <- build_1yr_country_return_factors(
  curve_models = baseline_curve_models,
  scenario_type = "baseline",
  scenario_name_prefix = "Baseline"
)

baseline_replay <- replay_1yr_return_factors(baseline_return_factors)
baseline_rung_summary <- baseline_replay$rung_history
baseline_country_bond_pl <- build_1yr_country_bond_pl(
  rung_summary = baseline_rung_summary,
  country_return_factors = baseline_country_return_factors
)

baseline_model_summary <- baseline_rung_summary %>%
  dplyr::group_by(model) %>%
  dplyr::summarise(
    final_active_members = dplyr::last(active_end_count),
    final_total_position = dplyr::last(active_position_end),
    final_average_position = dplyr::last(average_position_end),
    total_withdrawals = sum(total_withdrawal),
    total_withdrawal_penalties = sum(withdrawal_penalty),
    total_death_forfeited_position = sum(death_forfeited_position),
    average_gross_return_factor = mean(gross_return_factor),
    .groups = "drop"
  )

baseline_rung_summary
baseline_country_bond_pl
baseline_model_summary
```

## Shock Examples

These scenarios reuse the same deaths, withdrawals, and CIR withdrawal
intensity path as the baseline. Only the model-implied 1-year gross return
factors change.

```{r shock-specs}
shock_ramp_start_fraction <- -0.30 / length(2015:2020)

shock_examples <- list(
  global_l_neg30pct_2015 = list(
    label = "2015 Global L -30% Average Level",
    shock_year = 2015,
    shock_curves = curves,
    shock_factors = "L",
    shock_magnitude = -0.30,
    shock_basis = "average_level_fraction",
    shock_type = "additive"
  ),
  global_l_neg30pct_decay_2015_2020 = list(
    label = "Global L -30% average level linear decay 2015-2020",
    shock_profile = "linear_decay",
    shock_start_year = 2015,
    shock_start_anchor = "purchase_date",
    shock_end_year = 2020,
    shock_end_anchor = "purchase_date",
    shock_effect_timing = "full_window",
    shock_curves = curves,
    shock_factors = "L",
    shock_start_magnitude = -0.30,
    shock_end_magnitude = 0.0,
    shock_basis = "average_level_fraction",
    shock_type = "additive"
  ),
  global_l_neg30pct_increase_2015_2020 = list(
    label = "Global L increasing negative average level shock 2015-2020",
    shock_profile = "linear_increase",
    shock_start_year = 2015,
    shock_start_anchor = "purchase_date",
    shock_end_year = 2020,
    shock_end_anchor = "purchase_date",
    shock_effect_timing = "full_window",
    shock_curves = curves,
    shock_factors = "L",
    shock_start_magnitude = shock_ramp_start_fraction,
    shock_end_magnitude = -0.30,
    shock_basis = "average_level_fraction",
    shock_type = "additive"
  )
)
```

```{r shock-valuations}
shock_curve_models <- purrr::imap(shock_examples, function(shock_spec, shock_key) {
  tontine_fit_rolling_shocked_curve_models(
    yields = yields,
    valuation_windows = valuation_windows,
    curves = curves,
    mats = mats,
    mat_names = mat_names,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference_curve = reference_curve,
    shock_spec = shock_spec,
    mce_controls = mce_baseline_controls,
    mce_shock_controls = mce_shock_controls,
    include_models = shock_model_names,
    fit_seed = fit_seed
  )
})

shock_return_factors <- purrr::imap_dfr(shock_curve_models, function(curve_models, shock_key) {
  build_1yr_return_factors(
    curve_models = curve_models,
    scenario_type = "shock",
    scenario_name_prefix = shock_examples[[shock_key]]$label,
    shock_label = shock_examples[[shock_key]]$label
  ) %>%
    dplyr::mutate(shock_key = shock_key)
})

shock_country_return_factors <- purrr::imap_dfr(shock_curve_models, function(curve_models, shock_key) {
  build_1yr_country_return_factors(
    curve_models = curve_models,
    scenario_type = "shock",
    scenario_name_prefix = shock_examples[[shock_key]]$label,
    shock_label = shock_examples[[shock_key]]$label
  ) %>%
    dplyr::mutate(shock_key = shock_key)
})

shock_replays <- lapply(split(shock_return_factors, shock_return_factors$shock_key), replay_1yr_return_factors)
shock_rung_summary <- dplyr::bind_rows(lapply(names(shock_replays), function(shock_key) {
  shock_replays[[shock_key]]$rung_history %>%
    dplyr::mutate(shock_key = shock_key)
}))

shock_country_bond_pl <- purrr::imap_dfr(shock_replays, function(shock_replay, shock_key) {
  build_1yr_country_bond_pl(
    rung_summary = shock_replay$rung_history,
    country_return_factors = shock_country_return_factors %>%
      dplyr::filter(.data$shock_key == .env$shock_key)
  ) %>%
    dplyr::mutate(shock_key = shock_key)
})
```

```{r shock-summaries}
shock_rung_deltas <- shock_rung_summary %>%
  dplyr::left_join(
    baseline_rung_summary %>%
      dplyr::select(
        model, rung_id, purchase_year,
        baseline_average_position_end = average_position_end,
        baseline_active_position_end = active_position_end,
        baseline_gross_return_factor = gross_return_factor,
        baseline_maturity_proceeds = maturity_proceeds
      ),
    by = c("model", "rung_id", "purchase_year")
  ) %>%
  dplyr::mutate(
    delta_average_position_end = average_position_end - baseline_average_position_end,
    delta_active_position_end = active_position_end - baseline_active_position_end,
    delta_gross_return_factor = gross_return_factor - baseline_gross_return_factor,
    delta_maturity_proceeds = maturity_proceeds - baseline_maturity_proceeds
  )

shock_country_bond_pl_deltas <- shock_country_bond_pl %>%
  dplyr::left_join(
    baseline_country_bond_pl %>%
      dplyr::filter(.data$model %in% shock_model_names) %>%
      dplyr::select(
        model, country, rung_id, purchase_year,
        baseline_country_gross_return_factor = country_gross_return_factor,
        baseline_country_purchase_cost = country_purchase_cost,
        baseline_country_maturity_proceeds = country_maturity_proceeds,
        baseline_country_bond_profit_loss = country_bond_profit_loss
      ),
    by = c("model", "country", "rung_id", "purchase_year")
  ) %>%
  dplyr::mutate(
    delta_country_gross_return_factor =
      .data$country_gross_return_factor - .data$baseline_country_gross_return_factor,
    delta_country_purchase_cost =
      .data$country_purchase_cost - .data$baseline_country_purchase_cost,
    delta_country_maturity_proceeds =
      .data$country_maturity_proceeds - .data$baseline_country_maturity_proceeds,
    delta_country_bond_profit_loss =
      .data$country_bond_profit_loss - .data$baseline_country_bond_profit_loss
  )

shock_affected_years <- function(shock_spec) {
  if (identical(shock_spec$shock_profile, "linear_decay") ||
      identical(shock_spec$shock_profile, "linear_increase")) {
    return(seq.int(shock_spec$shock_start_year, shock_spec$shock_end_year))
  }

  shock_spec$shock_year
}

shock_affected_year_lookup <- purrr::imap_dfr(shock_examples, function(shock_spec, shock_key) {
  tibble::tibble(
    shock_key = shock_key,
    purchase_year = shock_affected_years(shock_spec)
  )
})

shock_position_display <- shock_rung_deltas %>%
  dplyr::inner_join(shock_affected_year_lookup, by = c("shock_key", "purchase_year")) %>%
  dplyr::select(
    shock_label, model, purchase_year, active_end_count,
    gross_return_factor, baseline_gross_return_factor, delta_gross_return_factor,
    average_position_end, baseline_average_position_end, delta_average_position_end,
    active_position_end, baseline_active_position_end, delta_active_position_end
  ) %>%
  dplyr::arrange(shock_label, model, purchase_year)

shock_position_display
shock_country_bond_pl_deltas %>%
  dplyr::inner_join(shock_affected_year_lookup, by = c("shock_key", "purchase_year")) %>%
  dplyr::select(
    shock_label, model, country, purchase_year,
    country_bond_profit_loss, baseline_country_bond_profit_loss,
    delta_country_bond_profit_loss
  ) %>%
  dplyr::arrange(shock_label, country, model, purchase_year)
```

## Visualizations

```{r visualization-data}
model_levels <- c("Observed", "DNS", "DLY", "MCE")
model_palette <- c(
  Observed = "#7E6A9E",
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)
shock_model_palette <- model_palette[shock_model_names]
scenario_levels <- vapply(shock_examples, `[[`, character(1), "label")
shock_scenario_labels <- vapply(shock_examples, `[[`, character(1), "label")
year_breaks <- purchase_years

build_1yr_plot_y_limits <- function(values, symmetric = FALSE) {
  values <- values[is.finite(values)]
  if (length(values) == 0) {
    return(c(-1, 1))
  }

  if (isTRUE(symmetric)) {
    max_abs <- max(abs(values), 0)
    if (max_abs == 0) {
      max_abs <- 1
    }
    max_abs <- max_abs * 1.05
    return(c(-max_abs, max_abs))
  }

  value_range <- range(c(0, values))
  if (diff(value_range) == 0) {
    return(value_range + c(-1, 1))
  }

  value_range + c(-1, 1) * diff(value_range) * 0.05
}

format_1yr_shock_label <- function(scenario_label) {
  if (identical(scenario_label, "2015 Global L -30% Average Level")) {
    "2015 Global -30% Average Level"
  } else if (identical(scenario_label, "Global L -30% average level linear decay 2015-2020")) {
    "Global -30% Average Level Decay"
  } else if (identical(scenario_label, "Global L increasing negative average level shock 2015-2020")) {
    "Global Increasing Negative Average Level"
  } else {
    scenario_label
  }
}

baseline_plot_data <- baseline_rung_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

baseline_country_plot_data <- baseline_country_bond_pl %>%
  dplyr::mutate(
    model = factor(.data$model, levels = model_levels),
    country = factor(.data$country, levels = curves)
  )

shock_plot_data <- shock_rung_deltas %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::mutate(
    model = factor(.data$model, levels = shock_model_names),
    shock_label = factor(.data$shock_label, levels = scenario_levels)
  )

shock_country_plot_data <- shock_country_bond_pl_deltas %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::mutate(
    model = factor(.data$model, levels = shock_model_names),
    country = factor(.data$country, levels = curves),
    shock_label = factor(.data$shock_label, levels = scenario_levels)
  )

baseline_country_bond_pl_y_limits <- build_1yr_plot_y_limits(
  baseline_country_plot_data$country_bond_profit_loss,
  symmetric = TRUE
)
shock_bond_pl_delta_y_limits <- build_1yr_plot_y_limits(
  shock_country_plot_data$delta_country_bond_profit_loss,
  symmetric = TRUE
)
survivor_payout_delta_y_limits <- build_1yr_plot_y_limits(
  shock_plot_data$delta_average_position_end,
  symmetric = TRUE
)

build_1yr_average_position_plot <- function(plot_data) {
  ggplot2::ggplot(
    plot_data,
    ggplot2::aes(x = purchase_year, y = average_position_end, color = model)
  ) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = purchase_years) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = "Baseline Reinvested Position per Active Member",
      x = "Purchase Year",
      y = "Average Active Position",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_withdrawal_penalty_plot <- function(plot_data) {
  ggplot2::ggplot(
    plot_data,
    ggplot2::aes(x = purchase_year, y = withdrawal_penalty)
  ) +
    ggplot2::geom_col(fill = "#4C78A8", width = 0.7) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = purchase_years) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = "Common Withdrawal Penalties by Rung",
      x = "Purchase Year",
      y = "Withdrawal Penalty Generated"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_shocked_position_plot <- function(plot_data, scenario_label) {
  filtered_plot_data <- plot_data %>%
    dplyr::filter(.data$shock_label == scenario_label)

  ggplot2::ggplot(
    filtered_plot_data,
    ggplot2::aes(x = purchase_year, y = delta_average_position_end, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = purchase_years) +
    ggplot2::scale_y_continuous(
      labels = scales::dollar_format(),
      limits = survivor_payout_delta_y_limits
    ) +
    ggplot2::labs(
      title = paste("Shock Survivor Payout Delta:", format_1yr_shock_label(scenario_label)),
      x = "Purchase Year",
      y = "Change in Survivor Payout per Member",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_country_baseline_bond_pl_plot <- function(plot_data, country_name) {
  country_label <- toupper(country_name)

  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$country == .env$country_name),
    ggplot2::aes(x = purchase_year, y = country_bond_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = purchase_years) +
    ggplot2::scale_y_continuous(
      labels = scales::dollar_format(),
      limits = baseline_country_bond_pl_y_limits
    ) +
    ggplot2::labs(
      title = paste("Baseline Bond P/L:", country_label),
      x = "Purchase Year",
      y = "Country Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_1yr_country_shock_bond_pl_plot <- function(plot_data, scenario_label, country_name) {
  filtered_plot_data <- plot_data %>%
    dplyr::filter(
      .data$shock_label == scenario_label,
      .data$country == country_name
    )

  ggplot2::ggplot(
    filtered_plot_data,
    ggplot2::aes(x = purchase_year, y = delta_country_bond_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = shock_model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = year_breaks, minor_breaks = purchase_years) +
    ggplot2::scale_y_continuous(
      labels = scales::dollar_format(),
      limits = shock_bond_pl_delta_y_limits
    ) +
    ggplot2::labs(
      title = paste(
        "Shock Bond P/L Delta:",
        paste0(toupper(country_name), ","),
        format_1yr_shock_label(scenario_label)
      ),
      x = "Purchase Year",
      y = "Change in Country Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

country_baseline_bond_plots <- setNames(lapply(curves, function(country_name) {
  build_1yr_country_baseline_bond_pl_plot(baseline_country_plot_data, country_name)
}), curves)

country_shock_bond_plots <- purrr::imap(shock_scenario_labels, function(scenario_label, shock_key) {
  setNames(lapply(curves, function(country_name) {
    build_1yr_country_shock_bond_pl_plot(
      shock_country_plot_data,
      scenario_label,
      country_name
    )
  }), curves)
})
```

```{r plot-baseline-average-position}
build_1yr_average_position_plot(baseline_plot_data)
```

```{r plot-withdrawal-penalties}
build_1yr_withdrawal_penalty_plot(
  baseline_rung_summary %>%
    dplyr::filter(.data$model == "Observed")
)
```

```{r plot-baseline-country-bond-pl-usa}
country_baseline_bond_plots$usa
```

```{r plot-baseline-country-bond-pl-gbr}
country_baseline_bond_plots$gbr
```

```{r plot-baseline-country-bond-pl-jpn}
country_baseline_bond_plots$jpn
```

```{r plot-baseline-country-bond-pl-ger}
country_baseline_bond_plots$ger
```

```{r plot-shocked-position-global-2015}
build_1yr_shocked_position_plot(
  shock_plot_data,
  "2015 Global L -30% Average Level"
)
```

```{r plot-shock-country-bond-pl-global-2015-usa}
country_shock_bond_plots$global_l_neg30pct_2015$usa
```

```{r plot-shock-country-bond-pl-global-2015-gbr}
country_shock_bond_plots$global_l_neg30pct_2015$gbr
```

```{r plot-shock-country-bond-pl-global-2015-jpn}
country_shock_bond_plots$global_l_neg30pct_2015$jpn
```

```{r plot-shock-country-bond-pl-global-2015-ger}
country_shock_bond_plots$global_l_neg30pct_2015$ger
```

```{r plot-shocked-position-global-decay}
build_1yr_shocked_position_plot(
  shock_plot_data,
  "Global L -30% average level linear decay 2015-2020"
)
```

```{r plot-shock-country-bond-pl-global-decay-usa}
country_shock_bond_plots$global_l_neg30pct_decay_2015_2020$usa
```

```{r plot-shock-country-bond-pl-global-decay-gbr}
country_shock_bond_plots$global_l_neg30pct_decay_2015_2020$gbr
```

```{r plot-shock-country-bond-pl-global-decay-jpn}
country_shock_bond_plots$global_l_neg30pct_decay_2015_2020$jpn
```

```{r plot-shock-country-bond-pl-global-decay-ger}
country_shock_bond_plots$global_l_neg30pct_decay_2015_2020$ger
```

```{r plot-shocked-position-global-increase}
build_1yr_shocked_position_plot(
  shock_plot_data,
  "Global L increasing negative average level shock 2015-2020"
)
```

```{r plot-shock-country-bond-pl-global-increase-usa}
country_shock_bond_plots$global_l_neg30pct_increase_2015_2020$usa
```

```{r plot-shock-country-bond-pl-global-increase-gbr}
country_shock_bond_plots$global_l_neg30pct_increase_2015_2020$gbr
```

```{r plot-shock-country-bond-pl-global-increase-jpn}
country_shock_bond_plots$global_l_neg30pct_increase_2015_2020$jpn
```

```{r plot-shock-country-bond-pl-global-increase-ger}
country_shock_bond_plots$global_l_neg30pct_increase_2015_2020$ger
```

```{r country-scenario-bond-pl-display}
country_scenario_bond_pl_display <- shock_country_bond_pl_deltas %>%
  dplyr::filter(.data$model %in% shock_model_names) %>%
  dplyr::group_by(.data$shock_label, .data$model, .data$country) %>%
  dplyr::summarise(
    baseline_cumulative_country_bond_profit_loss =
      sum(.data$baseline_country_bond_profit_loss),
    shock_cumulative_country_bond_profit_loss =
      sum(.data$country_bond_profit_loss),
    cumulative_country_bond_profit_loss_delta =
      sum(.data$delta_country_bond_profit_loss),
    .groups = "drop"
  ) %>%
  dplyr::mutate(country = toupper(.data$country)) %>%
  dplyr::arrange(.data$shock_label, .data$country, .data$model)

country_scenario_bond_pl_display
```
