---
title: "Tontine Stress Test: Multi-Year Ladders"
date: "2026-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Purpose

This notebook extends the tontine bond-ladder application from annual 1Y ZCB
rungs to overlapping 2Y and 5Y ZCB rungs. The longer maturities keep existing
holdings exposed to rate moves after purchase, so the notebook separates
hold-to-maturity purchase economics from mark-to-market shock losses on
already-owned bonds.

```{r libraries}
library(here)
library(dplyr)
library(purrr)
library(ggplot2)
library(scales)
library(tibble)
library(vars)
library(tsDyn)
library(Matrix)

sys.source(here::here("applications", "tontine_helpers.R"), envir = .GlobalEnv)
tontine_source_project()
```

```{r configuration}
curve_files <- list(
  usa = "usa-bs.csv",
  gbr = "gbr-bs.csv",
  jpn = "jpn-bs.csv",
  ger = "ger-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "usa"

mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- tontine_mat_names(mats)

data_start_date <- as.Date("2010-01-01")
data_end_date <- as.Date("2021-12-31")
lookback_years <- 1

lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)
fit_seed <- 999

mce_baseline_controls <- list(
  ECM_alpha = 0.2,
  X_trunc = TRUE,
  Xt_smooth = FALSE,
  smoother = NULL,
  CR_S0_shrink_diag = 0.4,
  CR_check_every = 10,
  CR_use_loglik = FALSE,
  CR_store_path = FALSE
)

mce_shock_controls <- list(
  reuse_ECM = TRUE,
  reuse_BS0 = TRUE,
  ECM_fallback = "baseline",
  anchor_shock_curves = FALSE
)

N_members <- 1000
target_total_ladder_par_per_member <- 100000
total_target_par <- N_members * target_total_ladder_par_per_member
population_seed <- fit_seed
q_full <- c(
  0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
  0.021506, 0.023614, 0.025473, 0.027789, 0.030319
)

maturity_specs <- list(
  `2Y` = list(bond_maturity_years = 2, purchase_years = 2011:2019),
  `5Y` = list(bond_maturity_years = 5, purchase_years = 2011:2016)
)
mtm_valuation_years <- 2015:2020
model_purchase_years <- sort(unique(c(
  unlist(lapply(maturity_specs, `[[`, "purchase_years")),
  mtm_valuation_years
)))

baseline_model_names <- c("Observed", "DNS", "DLY", "MCE")
shock_model_names <- c("DNS", "DLY", "MCE")
```

```{r data}
yields <- tontine_read_yields(
  curve_files = curve_files,
  start_date = data_start_date,
  end_date = data_end_date
)
```

```{r valuation-windows}
valuation_windows <- tontine_build_valuation_windows(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = model_purchase_years,
  lookback_years = lookback_years
)
```

```{r ladder-schedules}
build_multiyr_schedule <- function(spec, maturity_label) {
  purchase_years <- spec$purchase_years
  target_rung_par_per_member <- target_total_ladder_par_per_member / length(purchase_years)
  q <- q_full[seq_along(purchase_years)]
  population_simulation <- tontine_simulate_population(
    N_members = N_members,
    q = q,
    seed = population_seed + spec$bond_maturity_years
  )

  tontine_build_bond_ladder_schedule(
    yields = yields,
    reference_curve = reference_curve,
    purchase_years = purchase_years,
    curves = curves,
    total_target_par = total_target_par,
    q = q,
    population_simulation = population_simulation,
    target_rung_par_per_member = target_rung_par_per_member,
    bond_maturity_years = spec$bond_maturity_years
  ) %>%
    dplyr::mutate(ladder_maturity = maturity_label)
}

ladder_schedules <- purrr::imap(maturity_specs, build_multiyr_schedule)
```

```{r baseline-models}
set.seed(fit_seed)

baseline_curve_models <- tontine_fit_rolling_baseline_curve_models(
  yields = yields,
  valuation_windows = valuation_windows,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  mce_controls = mce_baseline_controls,
  include_models = baseline_model_names,
  fit_seed = fit_seed
)
```

```{r baseline-valuations}
tag_valuation <- function(valuation, maturity_label) {
  valuation$country_holdings <- valuation$country_holdings %>%
    dplyr::mutate(ladder_maturity = maturity_label)
  valuation$cash_accounts <- valuation$cash_accounts %>%
    dplyr::mutate(ladder_maturity = maturity_label)
  valuation
}

baseline_valuations <- purrr::imap(ladder_schedules, function(ladder_schedule, maturity_label) {
  tontine_price_baseline_models(
    baseline_curve_models = baseline_curve_models,
    ladder_schedule = ladder_schedule,
    mat_names = mat_names
  ) %>%
    tag_valuation(maturity_label)
})
```

## Shock Example

The rate-pain diagnostic uses a USA `+100 BPS` level-factor shock beginning at
the 2015 purchase date and linearly decaying to zero at the 2020 purchase date.
Only mark-to-market losses on already-owned 2Y and 5Y holdings are reported
here.

```{r shock-specs}
shock_examples <- list(
  usa_l_100bps_decay_2015_2020 = list(
    label = "USA L +100 BPS linear decay 2015-2020",
    shock_profile = "linear_decay",
    shock_start_year = 2015,
    shock_start_anchor = "purchase_date",
    shock_end_year = 2020,
    shock_end_anchor = "purchase_date",
    shock_curves = "usa",
    shock_factors = "L",
    shock_start_magnitude = 1.0,
    shock_end_magnitude = 0.0,
    shock_type = "additive"
  )
)
```

```{r shock-models}
shock_curve_models <- purrr::imap(shock_examples, function(shock_spec, shock_key) {
  tontine_fit_rolling_shocked_curve_models(
    yields = yields,
    valuation_windows = valuation_windows,
    curves = curves,
    mats = mats,
    mat_names = mat_names,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference_curve = reference_curve,
    shock_spec = shock_spec,
    mce_controls = mce_baseline_controls,
    mce_shock_controls = mce_shock_controls,
    include_models = shock_model_names,
    fit_seed = fit_seed
  )
})
```

```{r baseline-summaries}
tontine_summarize_rungs <- function(valuation) {
  valuation$country_holdings %>%
    dplyr::group_by(
      ladder_maturity, model, scenario, scenario_type, shock_label,
      rung_id, purchase_year, bond_maturity_years
    ) %>%
    dplyr::summarise(
      average_zero_rate = mean(zero_rate),
      total_purchase_cost = sum(purchase_cost),
      total_maturity_proceeds = sum(maturity_proceeds),
      .groups = "drop"
    ) %>%
    dplyr::left_join(
      valuation$cash_accounts %>%
        dplyr::select(
          ladder_maturity, model, scenario, rung_id,
          cash_end, rung_profit_loss, cumulative_profit_loss
        ),
      by = c("ladder_maturity", "model", "scenario", "rung_id")
    )
}

baseline_rung_summary <- purrr::imap_dfr(baseline_valuations, function(valuation, maturity_label) {
  tontine_summarize_rungs(valuation)
})

baseline_rung_summary
```

## Mark-to-Market Shock Loss

The mark-to-market section values only holdings that were purchased before each
annual shock valuation date and have not yet matured. This is the channel where
a positive rate shock lowers the value of already-owned longer-duration bonds.

```{r mtm-shock}
mtm_valuation_schedule <- valuation_windows %>%
  dplyr::filter(.data$purchase_year %in% mtm_valuation_years) %>%
  dplyr::transmute(
    valuation_year = .data$purchase_year,
    valuation_date = .data$purchase_date
  )

mtm_shock_deltas <- purrr::imap_dfr(baseline_valuations, function(valuation, maturity_label) {
  purrr::map2_dfr(
    mtm_valuation_schedule$valuation_year,
    mtm_valuation_schedule$valuation_date,
    function(valuation_year, valuation_date) {
      tontine_compare_mtm_shock(
        baseline_holdings = valuation$country_holdings,
        baseline_curve_models = baseline_curve_models,
        shocked_curve_models = shock_curve_models$usa_l_100bps_decay_2015_2020,
        mats = mats,
        mat_names = mat_names,
        valuation_date = valuation_date,
        shock_label = shock_examples$usa_l_100bps_decay_2015_2020$label
      ) %>%
        dplyr::mutate(
          ladder_maturity = maturity_label,
          valuation_year = valuation_year
        )
    }
  )
})

mtm_shock_summary <- mtm_shock_deltas %>%
  dplyr::group_by(ladder_maturity, model, valuation_year, valuation_date, purchase_year, shock_label) %>%
  dplyr::summarise(
    baseline_mtm_value = sum(mtm_value_baseline),
    shocked_mtm_value = sum(mtm_value_shocked),
    mtm_value_delta = sum(mtm_value_delta),
    mtm_value_delta_pct = mtm_value_delta / baseline_mtm_value,
    average_zero_rate_delta = mean(mtm_zero_rate_delta),
    .groups = "drop"
  )

mtm_total_by_valuation_year <- mtm_shock_summary %>%
  dplyr::group_by(ladder_maturity, model, valuation_year, valuation_date, shock_label) %>%
  dplyr::summarise(
    baseline_mtm_value = sum(baseline_mtm_value),
    shocked_mtm_value = sum(shocked_mtm_value),
    total_mtm_loss = sum(mtm_value_delta),
    total_mtm_loss_pct = total_mtm_loss / baseline_mtm_value,
    .groups = "drop"
  )

mtm_cumulative_cohort_summary <- mtm_shock_summary %>%
  dplyr::arrange(ladder_maturity, model, valuation_year, purchase_year) %>%
  dplyr::group_by(ladder_maturity, model, valuation_year, valuation_date, shock_label) %>%
  dplyr::mutate(
    cumulative_mtm_loss = cumsum(mtm_value_delta),
    cumulative_baseline_mtm_value = cumsum(baseline_mtm_value),
    cumulative_mtm_loss_pct = cumulative_mtm_loss / cumulative_baseline_mtm_value
  ) %>%
  dplyr::ungroup()

mtm_country_summary <- mtm_shock_deltas %>%
  dplyr::group_by(ladder_maturity, model, valuation_year, valuation_date, country, shock_label) %>%
  dplyr::summarise(
    baseline_mtm_value = sum(mtm_value_baseline),
    shocked_mtm_value = sum(mtm_value_shocked),
    country_mtm_loss = sum(mtm_value_delta),
    country_mtm_loss_pct = country_mtm_loss / baseline_mtm_value,
    average_zero_rate_delta = mean(mtm_zero_rate_delta),
    .groups = "drop"
  )

mtm_5y_gain_diagnostic <- mtm_shock_deltas %>%
  dplyr::filter(.data$ladder_maturity == "5Y", .data$valuation_year %in% 2015:2016) %>%
  dplyr::group_by(model, valuation_year, country) %>%
  dplyr::summarise(
    baseline_mtm_value = sum(mtm_value_baseline),
    shocked_mtm_value = sum(mtm_value_shocked),
    mtm_value_delta = sum(mtm_value_delta),
    average_zero_rate_delta = mean(mtm_zero_rate_delta),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    diagnostic_note = dplyr::case_when(
      mtm_value_delta > 0 & average_zero_rate_delta < 0 ~
        "MTM gain is driven by model-implied lower shocked remaining rates.",
      mtm_value_delta > 0 & average_zero_rate_delta >= 0 ~
        "MTM gain occurs despite higher average rates; inspect country/maturity mix.",
      TRUE ~ "MTM loss is directionally consistent with higher shocked remaining rates."
    )
  ) %>%
  dplyr::arrange(valuation_year, model, country)

mtm_shock_summary
mtm_cumulative_cohort_summary
mtm_total_by_valuation_year
mtm_country_summary
mtm_5y_gain_diagnostic
```

## Visualizations

```{r visualization-data}
model_levels <- c("Observed", "DNS", "DLY", "MCE")
model_palette <- c(
  Observed = "#7E6A9E",
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)

baseline_plot_data <- baseline_rung_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

mtm_plot_data <- mtm_shock_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

mtm_cumulative_plot_data <- mtm_cumulative_cohort_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

mtm_total_plot_data <- mtm_total_by_valuation_year %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

mtm_country_plot_data <- mtm_country_summary %>%
  dplyr::mutate(model = factor(model, levels = model_levels))

build_multiyr_baseline_plot <- function(plot_data, maturity_label) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$ladder_maturity == maturity_label),
    ggplot2::aes(x = purchase_year, y = rung_profit_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = paste("Baseline Bond P/L by Rung:", maturity_label),
      x = "Purchase Year",
      y = "Rung Bond P/L",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_mtm_cumulative_cohort_plot <- function(plot_data, maturity_label, valuation_year_value) {
  ggplot2::ggplot(
    plot_data %>%
      dplyr::filter(
        .data$ladder_maturity == maturity_label,
        .data$valuation_year == valuation_year_value
      ),
    ggplot2::aes(
      x = factor(purchase_year),
      y = cumulative_mtm_loss,
      fill = model
    )
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_col(position = ggplot2::position_dodge(width = 0.78), width = 0.7) +
    ggplot2::scale_fill_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = paste("Cumulative MTM Loss by Rung:", maturity_label, valuation_year_value),
      x = "Original Purchase Year",
      y = "Cumulative MTM Loss",
      fill = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_mtm_total_plot <- function(plot_data, maturity_label) {
  ggplot2::ggplot(
    plot_data %>% dplyr::filter(.data$ladder_maturity == maturity_label),
    ggplot2::aes(x = valuation_year, y = total_mtm_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = mtm_valuation_years) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = paste("Total MTM Loss by Shock Valuation Year:", maturity_label),
      x = "Shock Valuation Year",
      y = "Total MTM Loss",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

build_multiyr_country_mtm_plot <- function(plot_data, maturity_label, country_name) {
  ggplot2::ggplot(
    plot_data %>%
      dplyr::filter(
        .data$ladder_maturity == maturity_label,
        .data$country == country_name
      ),
    ggplot2::aes(x = valuation_year, y = country_mtm_loss, color = model)
  ) +
    ggplot2::geom_hline(yintercept = 0, color = "grey60", linewidth = 0.4) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::geom_point(size = 1.8) +
    ggplot2::scale_color_manual(values = model_palette, drop = FALSE) +
    ggplot2::scale_x_continuous(breaks = mtm_valuation_years) +
    ggplot2::scale_y_continuous(labels = scales::dollar_format()) +
    ggplot2::labs(
      title = paste("Country MTM Loss:", maturity_label, toupper(country_name)),
      x = "Shock Valuation Year",
      y = "Country MTM Loss",
      color = "Model"
    ) +
    ggplot2::theme_minimal()
}

mtm_cumulative_cohort_plots <- setNames(lapply(names(maturity_specs), function(maturity_label) {
  setNames(lapply(mtm_valuation_years, function(valuation_year_value) {
    build_multiyr_mtm_cumulative_cohort_plot(
      mtm_cumulative_plot_data,
      maturity_label,
      valuation_year_value
    )
  }), as.character(mtm_valuation_years))
}), names(maturity_specs))

mtm_country_plots <- setNames(lapply(names(maturity_specs), function(maturity_label) {
  setNames(lapply(curves, function(country_name) {
    build_multiyr_country_mtm_plot(mtm_country_plot_data, maturity_label, country_name)
  }), curves)
}), names(maturity_specs))
```

```{r plot-baseline-2y-rung-pl}
build_multiyr_baseline_plot(baseline_plot_data, "2Y")
```

```{r plot-baseline-5y-rung-pl}
build_multiyr_baseline_plot(baseline_plot_data, "5Y")
```

```{r plot-mtm-cumulative-cohort-loss-2y-2016}
mtm_cumulative_cohort_plots$`2Y`$`2016`
```

```{r plot-mtm-cumulative-cohort-loss-5y-2016}
mtm_cumulative_cohort_plots$`5Y`$`2016`
```

```{r plot-mtm-total-loss-2y}
build_multiyr_mtm_total_plot(mtm_total_plot_data, "2Y")
```

```{r plot-mtm-total-loss-5y}
build_multiyr_mtm_total_plot(mtm_total_plot_data, "5Y")
```

```{r plot-country-mtm-loss-2y-usa}
mtm_country_plots$`2Y`$usa
```

```{r plot-country-mtm-loss-5y-usa}
mtm_country_plots$`5Y`$usa
```
