---
title: "Ogden Cashflow Matching Baseline"
date: "2026-05-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Purpose

This notebook builds the Ogden baseline cashflow structure. The current version
only constructs deterministic liability cashflows, tenor-specific capped GMV
country weights, and an inception asset portfolio whose future cashflows match
the liability cashflows.

```{r libraries}
library(here)
library(dplyr)
library(purrr)
library(tibble)
library(ggplot2)
library(patchwork)
library(Matrix)
library(vars)
library(tsDyn)

sys.source(here::here("core_formatting.R"), envir = .GlobalEnv)
sys.source(here::here("applications", "tontine_helpers.R"), envir = .GlobalEnv)
sys.source(here::here("applications", "ogden_helpers.R"), envir = .GlobalEnv)
tontine_source_project()
```

```{r configuration}
curve_files <- list(
  gbr = "gbr-bs.csv",
  usa = "usa-bs.csv",
  ger = "ger-bs.csv",
  fra = "fra-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "gbr"

mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- tontine_mat_names(mats)

data_start_date <- as.Date("2010-01-01")
data_end_date <- as.Date("2021-12-31")

valuation_years <- 2011:2020
lookback_years <- 1
lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)
fit_seed <- 999
baseline_model_names <- c("DNS", "DLY", "MCE")

mce_baseline_controls <- list(
  ECM_alpha = 0.2,
  X_trunc = TRUE,
  Xt_smooth = FALSE,
  smoother = NULL,
  CR_S0_shrink_diag = 0.4,
  CR_check_every = 10,
  CR_use_loglik = FALSE,
  CR_store_path = FALSE
)

mce_shock_controls <- list(
  reuse_ECM = TRUE,
  reuse_BS0 = TRUE,
  ECM_fallback = "baseline"
)

M_0 <- 1000
liability_b0 <- 100000
liability_escalation_rate <- 0.02

payment_years <- 2011:2030
liability_horizons <- seq_along(payment_years)

q <- c(
  0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
  0.021506, 0.023614, 0.025473, 0.027789, 0.030319,
  0.033748, 0.037142, 0.042361, 0.046881, 0.052665,
  0.059666, 0.067996, 0.075244, 0.084093, 0.093857
)
stopifnot(length(q) == length(payment_years))

gmv_calibration_start <- as.Date("2010-01-01")
gmv_calibration_end <- as.Date("2011-01-01")
gmv_weight_floor <- 0.10
gmv_weight_ceiling <- 0.50
```

```{r data}
yields <- tontine_read_yields(
  curve_files = curve_files,
  start_date = data_start_date,
  end_date = data_end_date
)

asset_purchase_date <- tontine_first_observed_date(
  curve_df = yields[[reference_curve]],
  year_value = min(payment_years)
)

asset_purchase_date
```

```{r valuation-windows}
valuation_windows <- tontine_build_valuation_windows(
  yields = yields,
  reference_curve = reference_curve,
  purchase_years = valuation_years,
  lookback_years = lookback_years,
  date_position = "last"
)

valuation_windows %>%
  transmute(
    valuation_index = rung_id,
    valuation_year = purchase_year,
    valuation_date = purchase_date,
    estimation_start,
    estimation_end,
    n_reference_observations
  )
```

## Liability Cashflows

Claimant counts use the multiplicative survival convention. Per-claimant
payments follow \(b_k = b_0(1 + g_b)^k\).

```{r liability-cashflows}
liability_cashflows <- ogden_build_liability_cashflows(
  M_0 = M_0,
  q = q,
  b0 = liability_b0,
  g_b = liability_escalation_rate,
  payment_years = payment_years
)

liability_cashflows
```

## Capped GMV Weights

Country allocations are estimated tenor-by-tenor from zero-coupon bond
log-return covariance over 2010-01-01 through 2011-01-01. Each country weight is
constrained to lie between 10% and 50%.

```{r gmv-weights}
cashflow_gmv_weights <- ogden_estimate_gmv_weights(
  yields = yields,
  curves = curves,
  horizons = liability_horizons,
  start_date = gmv_calibration_start,
  end_date = gmv_calibration_end,
  mats = mats,
  mat_names = mat_names,
  weight_floor = gmv_weight_floor,
  weight_ceiling = gmv_weight_ceiling
)

cashflow_gmv_weights
```

## Cashflow-Matched Asset Portfolio

At the first trading day of 2011, the asset portfolio purchases country-specific
zero-coupon instruments for each liability horizon. For each horizon, country
par values are set by the capped GMV weights, and total par equals the
corresponding liability cashflow.

```{r asset-portfolio}
observed_asset_portfolio <- ogden_build_cashflow_matched_assets(
  liability_cashflows = liability_cashflows,
  portfolio_weights = cashflow_gmv_weights,
  curve_panels = yields,
  purchase_date = asset_purchase_date,
  mats = mats,
  mat_names = mat_names
)

asset_cashflow_match_summary <- ogden_summarise_asset_cashflow_match(
  observed_asset_portfolio
)

asset_purchase_summary <- ogden_summarise_asset_purchase(observed_asset_portfolio)

observed_asset_portfolio
asset_cashflow_match_summary
asset_purchase_summary
```

## Baseline Model Valuations

DNS and DLY models are estimated over annual one-year lookback windows. Asset
and liability values are measured immediately before the annual cashflow date,
so the current-year cashflow is included at par.

```{r baseline-model-fits}
baseline_curve_models <- tontine_fit_rolling_baseline_curve_models(
  yields = yields,
  valuation_windows = valuation_windows,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  mce_controls = mce_baseline_controls,
  include_models = baseline_model_names,
  fit_seed = fit_seed
)

baseline_fit_summary <- imap_dfr(baseline_curve_models, function(model_obj, model_key) {
  tibble(
    model = model_obj$model,
    n_windows = length(model_obj$fit),
    first_valuation_year = min(model_obj$valuation_windows$purchase_year),
    last_valuation_year = max(model_obj$valuation_windows$purchase_year),
    curves = paste(toupper(curves), collapse = ", "),
    reference_curve = toupper(reference_curve)
  )
})

baseline_fit_summary
```

```{r baseline-model-valuations}
baseline_curve_panel_sets <- ogden_build_curve_panel_sets(
  observed_yields = yields,
  baseline_curve_models = baseline_curve_models,
  model_order = c("Observed", "DNS", "DLY", "MCE")
)

baseline_asset_valuation_summary <- ogden_value_assets_by_model(
  asset_portfolio = observed_asset_portfolio,
  valuation_windows = valuation_windows,
  curve_panel_sets = baseline_curve_panel_sets,
  curves = curves,
  mats = mats,
  mat_names = mat_names
)

baseline_liability_valuation_summary <- ogden_value_liabilities_by_model(
  liability_cashflows = liability_cashflows,
  valuation_windows = valuation_windows,
  portfolio_weights = cashflow_gmv_weights,
  curve_panel_sets = baseline_curve_panel_sets,
  curves = curves,
  mats = mats,
  mat_names = mat_names
)

baseline_valuation_summary <- ogden_summarise_model_valuations(
  asset_valuation_summary = baseline_asset_valuation_summary,
  liability_valuation_summary = baseline_liability_valuation_summary
)

baseline_asset_valuation_summary
baseline_liability_valuation_summary
baseline_valuation_summary
```

## Baseline Surplus / Shortfall

```{r baseline-surplus-shortfall-plot, fig.width=10, fig.height=6}
ogden_full_model_palette <- c(
  Observed = "#7E6A9E",
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)

baseline_surplus_shortfall_plot_data <- baseline_valuation_summary %>%
  mutate(model = factor(model, levels = c("Observed", "DNS", "DLY", "MCE")))

baseline_surplus_shortfall_y_limit <- max(
  abs(baseline_surplus_shortfall_plot_data$surplus_loss),
  na.rm = TRUE
)

ogden_baseline_surplus_shortfall_plot <- ggplot(
  baseline_surplus_shortfall_plot_data,
  aes(x = valuation_year, y = surplus_loss, color = model)
) +
  geom_hline(yintercept = 0, color = "grey40", linewidth = 0.35) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_color_manual(values = ogden_full_model_palette, drop = FALSE) +
  scale_x_continuous(breaks = valuation_years) +
  scale_y_continuous(
    labels = scales::dollar,
    limits = c(
      -baseline_surplus_shortfall_y_limit,
      baseline_surplus_shortfall_y_limit
    )
  ) +
  labs(
    title = "Insurer Portfolio Baseline Surplus / Shortfall by Year",
    x = "Valuation Year",
    y = "Surplus / Shortfall",
    color = "Model"
  ) +
  theme_minimal() +
  theme(legend.position = "right")

ogden_baseline_surplus_shortfall_plot
```

## Persistent GBR Level Shock

The first shock experiment applies a persistent latent level-factor shock to GBR
from the 2012 annual lookback window onward. The scaffold supports -100 BPS and
-200 BPS shocks and valuation reporting from 2013 through 2020. To keep
execution lightweight while testing, `active_shock_key` and
`active_reporting_years` select the single shock/year subset to fit.

```{r gbr-persistent-shock-setup}
shock_reporting_years <- 2013:2015
active_shock_key <- "gbr_l_neg200bps_2012_2015"
active_reporting_years <- shock_reporting_years

shock_fit_windows <- valuation_windows %>%
  filter(purchase_year %in% c(2012, active_reporting_years))

shock_reporting_windows <- valuation_windows %>%
  filter(purchase_year %in% active_reporting_years)

gbr_persistent_shock_specs <- list(
  gbr_l_neg100bps_2012_2015 = list(
    label = "GBR L -100 BPS 2012-2015",
    shock_start_year = 2012,
    shock_start_anchor = "estimation_start",
    shock_end_year = max(active_reporting_years),
    shock_end_anchor = "estimation_end",
    shock_profile = "linear_decay",
    shock_start_magnitude = -1,
    shock_end_magnitude = -1,
    shock_effect_timing = "calendar",
    shock_curves = "gbr",
    shock_factors = "L",
    shock_magnitude = -1,
    shock_type = "additive"
  ),
  gbr_l_neg200bps_2012_2015 = list(
    label = "GBR L -200 BPS 2012-2015",
    shock_start_year = 2012,
    shock_start_anchor = "estimation_start",
    shock_end_year = max(active_reporting_years),
    shock_end_anchor = "estimation_end",
    shock_profile = "linear_decay",
    shock_start_magnitude = -2,
    shock_end_magnitude = -2,
    shock_effect_timing = "calendar",
    shock_curves = "gbr",
    shock_factors = "L",
    shock_magnitude = -2,
    shock_type = "additive"
  )
)

active_shock_spec <- gbr_persistent_shock_specs[[active_shock_key]]
active_shock_specs <- gbr_persistent_shock_specs[active_shock_key]

liability_dislocation_gamma <- 0.50
liability_dislocation_psi_1 <- abs(active_shock_spec$shock_magnitude) / 100 *
  liability_dislocation_gamma
liability_dislocation_psi_2 <- 0

liability_dislocation_gamma_scenarios <- tibble(
  dislocation_case = c("0.25x shock magnitude", "0.50x shock magnitude"),
  gamma_value = c(0.25, 0.50),
  psi_1 = abs(active_shock_spec$shock_magnitude) / 100 *
    gamma_value,
  psi_2 = 0
)

mce_dislocation_scale_scenarios <- tibble(
  valuation_case = c("Shocked exogenous dislocation", "Shocked hybrid dislocation"),
  mce_scale_case = c(
    "0.00x MCE residual transmission",
    "1.00x MCE residual transmission"
  ),
  mce_scale_value = c(0.00, 1.00)
)

gbr_persistent_shock_specs
active_shock_key
active_reporting_years
shock_fit_windows
shock_reporting_windows
liability_dislocation_gamma_scenarios
mce_dislocation_scale_scenarios
```

```{r gbr-persistent-shock-fits}
set.seed(fit_seed)

gbr_persistent_shock_curve_models <- purrr::imap(active_shock_specs, function(shock_spec, shock_key) {
  tontine_fit_rolling_shocked_curve_models(
    yields = yields,
    valuation_windows = shock_fit_windows,
    curves = curves,
    mats = mats,
    mat_names = mat_names,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference_curve = reference_curve,
    shock_spec = shock_spec,
    mce_controls = mce_baseline_controls,
    mce_shock_controls = mce_shock_controls,
    include_models = baseline_model_names,
    fit_seed = fit_seed
  )
})

names(gbr_persistent_shock_curve_models)
```

```{r gbr-persistent-shock-valuations}
gbr_persistent_shock_valuation_summary <- purrr::imap_dfr(
  gbr_persistent_shock_curve_models,
  function(shock_models, shock_key) {
    shock_spec <- gbr_persistent_shock_specs[[shock_key]]
    shock_curve_panel_sets <- ogden_build_curve_panel_sets(
      observed_yields = yields,
      baseline_curve_models = shock_models,
      model_order = baseline_model_names
    )

    shock_asset_values <- ogden_value_assets_by_model(
      asset_portfolio = observed_asset_portfolio,
      valuation_windows = shock_reporting_windows,
      curve_panel_sets = shock_curve_panel_sets,
      curves = curves,
      mats = mats,
      mat_names = mat_names
    )

    shock_liability_values <- ogden_value_liabilities_by_model(
      liability_cashflows = liability_cashflows,
      valuation_windows = shock_reporting_windows,
      portfolio_weights = cashflow_gmv_weights,
      curve_panel_sets = shock_curve_panel_sets,
      curves = curves,
      mats = mats,
      mat_names = mat_names
    )

    shock_liability_values_with_dislocation <- ogden_value_liabilities_by_model(
      liability_cashflows = liability_cashflows,
      valuation_windows = shock_reporting_windows,
      portfolio_weights = cashflow_gmv_weights,
      curve_panel_sets = shock_curve_panel_sets,
      curves = curves,
      mats = mats,
      mat_names = mat_names,
      psi_1 = liability_dislocation_psi_1,
      psi_2 = liability_dislocation_psi_2,
      psi_max_horizon = max(liability_horizons)
    )

    ogden_summarise_model_valuations(
      asset_valuation_summary = shock_asset_values,
      liability_valuation_summary = shock_liability_values
    ) %>%
      rename(
        market_liability_present_value = liability_present_value,
        market_surplus_loss = surplus_loss,
        market_funding_ratio = funding_ratio
      ) %>%
      left_join(
        shock_liability_values_with_dislocation %>%
          dplyr::select(
            model,
            valuation_index,
            valuation_year,
            valuation_date,
            liability_present_value_with_dislocation = liability_present_value
          ),
        by = c("model", "valuation_index", "valuation_year", "valuation_date")
      ) %>%
      mutate(
        liability_present_value = liability_present_value_with_dislocation,
        surplus_loss = asset_present_value - liability_present_value,
        funding_ratio = asset_present_value / liability_present_value,
        liability_dislocation_increment =
          liability_present_value_with_dislocation - market_liability_present_value
      ) %>%
      dplyr::select(-liability_present_value_with_dislocation) %>%
      mutate(
        shock_key = shock_key,
        shock_label = shock_spec$label,
        .before = 1
      )
  }
)

gbr_persistent_shock_delta_summary <- gbr_persistent_shock_valuation_summary %>%
  inner_join(
    baseline_valuation_summary %>%
      filter(valuation_year %in% shock_reporting_windows$purchase_year, model %in% baseline_model_names) %>%
      dplyr::select(
        model,
        valuation_year,
        baseline_asset_present_value = asset_present_value,
        baseline_liability_present_value = liability_present_value,
        baseline_surplus_loss = surplus_loss,
        baseline_funding_ratio = funding_ratio
      ),
    by = c("model", "valuation_year")
  ) %>%
  mutate(
    asset_pv_delta = asset_present_value - baseline_asset_present_value,
    liability_pv_delta = liability_present_value - baseline_liability_present_value,
    market_liability_pv_delta =
      market_liability_present_value - baseline_liability_present_value,
    surplus_delta = surplus_loss - baseline_surplus_loss,
    market_surplus_delta = market_surplus_loss - baseline_surplus_loss,
    funding_ratio_delta = funding_ratio - baseline_funding_ratio
  ) %>%
  arrange(shock_key, model)

gbr_persistent_shock_valuation_summary
gbr_persistent_shock_delta_summary
```

## 2013 Shock Liability Dislocation Sensitivity

This block tests shocked liability dislocations for the 2013 window only. The
MCE residual-transmission mechanism is used as a pseudo-independent dislocation
generator, and the resulting dislocation panel is applied to liability valuation
under DNS, DLY, and MCE model curves. The exogenous case uses the same hybrid
machinery with MCE scale set to zero.

```{r mce-model-based-dislocation-2013}
mce_model_dislocation_test_windows <- shock_reporting_windows

active_shock_models <- gbr_persistent_shock_curve_models[[active_shock_key]]

shock_model_curve_panel_sets <- ogden_build_curve_panel_sets(
  observed_yields = yields,
  baseline_curve_models = active_shock_models,
  model_order = baseline_model_names
)

shock_model_assets <- ogden_value_assets_by_model(
  asset_portfolio = observed_asset_portfolio,
  valuation_windows = mce_model_dislocation_test_windows,
  curve_panel_sets = shock_model_curve_panel_sets,
  curves = curves,
  mats = mats,
  mat_names = mat_names
)

mce_dislocation_sensitivity_grid <- tidyr::crossing(
  liability_dislocation_gamma_scenarios,
  mce_dislocation_scale_scenarios
)

mce_dislocation_sensitivity_comparison <- purrr::pmap_dfr(
  mce_dislocation_sensitivity_grid,
  function(dislocation_case, gamma_value, psi_1, psi_2,
           valuation_case, mce_scale_case, mce_scale_value) {
    gamma_mce_psi_panel <- ogden_shock_psi(
      baseline_mce_model = baseline_curve_models$MCE,
      shocked_mce_model = active_shock_models$MCE,
      valuation_windows = mce_model_dislocation_test_windows,
      curves = curves,
      mats = mats,
      mat_names = mat_names,
      reference_curve = reference_curve,
      liability_horizons = 0:max(liability_horizons),
      dislocation_scale = mce_scale_value
    )

    gamma_hybrid_psi_panel <- ogden_hybrid_shock_psi(
      mce_psi_panel = gamma_mce_psi_panel,
      exogenous_psi_1 = psi_1,
      exogenous_psi_2 = psi_2,
      psi_max_horizon = max(liability_horizons)
    )

    gamma_hybrid_psi_panel_by_model <- purrr::map_dfr(
      baseline_model_names,
      function(model_name) {
        gamma_hybrid_psi_panel %>%
          mutate(model = model_name)
      }
    )

    gamma_hybrid_liabilities <- ogden_value_liabilities_by_model(
      liability_cashflows = liability_cashflows,
      valuation_windows = mce_model_dislocation_test_windows,
      portfolio_weights = cashflow_gmv_weights,
      curve_panel_sets = shock_model_curve_panel_sets,
      curves = curves,
      mats = mats,
      mat_names = mat_names,
      psi_panel = gamma_hybrid_psi_panel_by_model
    )

    ogden_summarise_model_valuations(
      asset_valuation_summary = shock_model_assets,
      liability_valuation_summary = gamma_hybrid_liabilities
    ) %>%
      mutate(valuation_case = valuation_case, .before = 1) %>%
      mutate(
        dislocation_case = dislocation_case,
        dislocation_gamma = gamma_value,
        mce_scale_case = mce_scale_case,
        mce_dislocation_scale = mce_scale_value,
        shock_key = active_shock_key,
        shock_label = active_shock_spec$label,
        shock_bps = active_shock_spec$shock_magnitude * 100,
        .before = 1
      )
  }
) %>%
  mutate(
    valuation_case = factor(
      valuation_case,
      levels = c(
        "Shocked exogenous dislocation",
        "Shocked hybrid dislocation"
      )
    )
  ) %>%
  arrange(dislocation_gamma, mce_dislocation_scale, valuation_case) %>%
  mutate(valuation_case = as.character(valuation_case))

mce_dislocation_sensitivity_deltas <- mce_dislocation_sensitivity_comparison %>%
  inner_join(
    baseline_valuation_summary %>%
      filter(valuation_year %in% active_reporting_years, model %in% baseline_model_names) %>%
      dplyr::select(
        model,
        valuation_year,
        baseline_asset_present_value = asset_present_value,
        baseline_liability_present_value = liability_present_value,
        baseline_surplus_loss = surplus_loss,
        baseline_funding_ratio = funding_ratio
      ),
    by = c("model", "valuation_year")
  ) %>%
  transmute(
    shock_key,
    shock_label,
    shock_bps,
    valuation_year,
    model,
    dislocation_case,
    valuation_case,
    asset_pv_delta = asset_present_value - baseline_asset_present_value,
    liability_pv_delta = liability_present_value - baseline_liability_present_value,
    surplus_loss_delta = surplus_loss - baseline_surplus_loss,
    funding_ratio_delta = funding_ratio - baseline_funding_ratio
  ) %>%
  arrange(dislocation_case, valuation_case, model)

mce_dislocation_sensitivity_comparison
mce_dislocation_sensitivity_deltas
```

## Shock Valuation Delta Plots

```{r shock-valuation-delta-plots, fig.width=12, fig.height=8}
shock_delta_plot_data <- mce_dislocation_sensitivity_deltas %>%
  mutate(
    model = factor(model, levels = c("DNS", "DLY", "MCE")),
    valuation_year = factor(valuation_year),
    valuation_case = recode(
      valuation_case,
      "Shocked exogenous dislocation" = "Exogenous",
      "Shocked hybrid dislocation" = "Hybrid"
    ),
    scenario_label = paste(dislocation_case, valuation_case, sep = ", ")
  )

ogden_model_palette <- c(
  DNS = "#4C78A8",
  DLY = "#59A14F",
  MCE = "#C94C4C"
)

ogden_asset_liability_delta_y_limits <- c(0, 200000000)
ogden_surplus_shortfall_delta_y_limits <- c(-60000000, 5000000)

asset_liability_delta_plot_data <- shock_delta_plot_data %>%
  dplyr::select(
    valuation_year,
    model,
    scenario_label,
    asset_pv_delta,
    liability_pv_delta
  ) %>%
  tidyr::pivot_longer(
    cols = c(asset_pv_delta, liability_pv_delta),
    names_to = "delta_type",
    values_to = "pv_delta"
  ) %>%
  mutate(
    delta_type = recode(
      delta_type,
      asset_pv_delta = "Asset PV Delta",
      liability_pv_delta = "Liability PV Delta"
    )
  )

ogden_asset_liability_delta_plot <- ggplot(
  asset_liability_delta_plot_data,
  aes(x = model, y = pv_delta, fill = delta_type)
) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  facet_grid(valuation_year ~ scenario_label) +
  scale_y_continuous(
    labels = function(x) paste0("$", x / 1000000),
    limits = ogden_asset_liability_delta_y_limits
  ) +
  labs(
    title = "Asset vs Liability PV Delta by Shock Scenario",
    x = "Model",
    y = "PV Delta ($MM)",
    fill = "PV Type"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 26.4),
    axis.title = element_text(size = 22),
    axis.text = element_text(size = 15.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 15.5),
    legend.title = element_text(size = 13),
    strip.text = element_text(size = 14)
  )

ogden_surplus_delta_plot <- ggplot(
  shock_delta_plot_data,
  aes(x = model, y = surplus_loss_delta, fill = model)
) +
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_hline(yintercept = 0, color = "grey40", linewidth = 0.3) +
  facet_grid(valuation_year ~ scenario_label) +
  scale_fill_manual(values = ogden_model_palette, drop = FALSE) +
  scale_y_continuous(
    breaks = c(0, -20000000, -40000000, -60000000),
    labels = function(x) {
      ifelse(x < 0, paste0("-$", abs(x) / 1000000), paste0("$", x / 1000000))
    },
    limits = ogden_surplus_shortfall_delta_y_limits
  ) +
  labs(
    title = "Surplus / Shortfall Delta by Shock Scenario",
    x = "Model",
    y = "Surplus / Shortfall Delta ($MM)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 26.4),
    axis.title = element_text(size = 22),
    axis.text = element_text(size = 15.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 15.5),
    strip.text = element_text(size = 14)
  )

ogden_shock_delta_plot <- ogden_asset_liability_delta_plot /
  ogden_surplus_delta_plot +
  plot_layout(heights = c(1, 1))

ogden_shock_delta_plot
```
