---
title: "Case_Study_Tontine"
date: "2026-04-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Tontine Bond Ladder Example

This notebook builds the static tontine bond ladder case study appearing in section 6.2 of CCIRST. 

- A single valuation date `T_0` is chosen inside the sample.
- All model fits use only data available on or before `T_0`.
- The estimation window is a fixed 2-calendar-year lookback ending at `T_0`.
- The payout ladder is capped at the observed sample end date.
- The ladder engine is model-agnostic.
- Baseline ladder values are constructed from:
  - individual DNS fits per curve,
  - the DLY model,
  - the MCE model.

```{r libraries, warning = FALSE}
library(here)
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(scales)
library(vars)
library(tsDyn)
library(Matrix)

load_tontine_modules <- function() {
  project_files <- c(
    "core_formatting.R",
    "yield_estimation/curve_reformat.R",
    "yield_estimation/matrix_helpers.R",
    "yield_estimation/cr_core_estim.R",
    "yield_estimation/cr_eval.R",
    "yield_estimation/bl_single_curve.R",
    "yield_estimation/dly_mcm.R",
    "yield_estimation/bl_feature_extract.R",
    "yield_estimation/bl_normalize.R",
    "yield_estimation/bl_cross_estimation.R",
    "stress_testing/st_build_shock.R",
    "stress_testing/st_fit_shock.R"
  )

  invisible(lapply(project_files, function(path) {
    sys.source(here::here(path), envir = .GlobalEnv)
  }))
}

load_tontine_modules()
```

```{r model-config}
curve_files <- list(
  usa = "usa-bs.csv",
  gbr = "gbr-bs.csv",
  jpn = "jpn-bs.csv",
  ger = "ger-bs.csv"
)

curves <- names(curve_files)
reference_curve <- "usa"
mats <- c(1, 3, 6, 12, 24, 60, 84, 120, 240, 360)
mat_names <- paste0("X", unname(vapply(mats, numeric_to_matname, character(1))))

start_date <- as.Date("2010-01-01")
end_date <- as.Date("2020-12-31")
valuation_year <- 2015
lookback_years <- 2
estimation_start <- as.Date(sprintf("%d-01-01", valuation_year - lookback_years))
lambdas <- seq(0.01, 0.15, by = 0.005)
cutoffs <- c(4, 8)

dly_component <- "propagated_full"

mce_run_spec <- list(
  x_trunc = TRUE,
  xt_smooth = FALSE,
  smoother = NULL,
  hp_lambda = NULL,
  cov_shrink_diag = 0.4
)

shock_specs <- list(
  usa_l_1 = list(
    label = "USA L +1.0",
    shock_type = "additive",
    shock_curves = "usa",
    shock_factors = "L",
    shock_magnitude = 1.0,
    shock_window = NULL,
    reuse_BS0 = TRUE,
    reuse_ECM = TRUE
  ),
  usa_l_2 = list(
    label = "USA L +2.0",
    shock_type = "additive",
    shock_curves = "usa",
    shock_factors = "L",
    shock_magnitude = 2.0,
    shock_window = NULL,
    reuse_BS0 = TRUE,
    reuse_ECM = TRUE
  )
)

yields <- lapply(curve_files, function(file_name) {
  read.csv(here::here("reconstructed_data", file_name), stringsAsFactors = FALSE)
})

yields <- lapply(yields, function(curve_df) {
  curve_df %>%
    dplyr::filter(
      as.Date(time) >= start_date,
      as.Date(time) <= end_date
    ) %>%
    dplyr::mutate(time = as.Date(time)) %>%
    dplyr::arrange(time)
})
```

```{r ladder-config}
N_members <- 1000
target_total_payout_per_member <- 100000
country_weights <- rep(1 / length(curves), length(curves))
names(country_weights) <- curves

q <- c(0.013404, 0.014795, 0.016280, 0.017595, 0.019527,
       0.021506, 0.023614, 0.025473, 0.027789, 0.030319)

payout_years <- 2016:2020
n_rungs <- length(payout_years)
q <- q[seq_len(n_rungs)]

stopifnot(length(q) == n_rungs, max(payout_years) <= as.integer(format(end_date, "%Y")))
```

```{r helpers}
first_window_date <- function(curve_df, year_value) {
  curve_df %>%
    dplyr::filter(format(time, "%Y") == as.character(year_value)) %>%
    dplyr::arrange(time) %>%
    dplyr::slice(1) %>%
    dplyr::pull(time)
}

filter_estimation_window <- function(yields, start_date, end_date) {
  setNames(lapply(yields, function(curve_df) {
    curve_df %>%
      dplyr::filter(time >= start_date, time <= end_date) %>%
      dplyr::arrange(time)
  }), names(yields))
}

extract_curve_row <- function(curve_df, target_date) {
  out <- curve_df %>%
    dplyr::filter(time == target_date) %>%
    dplyr::slice(1)

  if (nrow(out) != 1) {
    stop("Curve snapshot could not be extracted at the requested valuation date.")
  }

  return(out)
}

extract_curve_snapshot_list <- function(curve_panels, target_date, curves) {
  setNames(lapply(curves, function(curve_name) {
    extract_curve_row(curve_panels[[curve_name]], target_date)
  }), curves)
}

curve_fit_to_panel <- function(time_index, fitted_matrix, mat_names) {
  out <- data.frame(time = as.Date(time_index), as.data.frame(fitted_matrix))
  colnames(out) <- c("time", mat_names)
  return(out)
}

split_curve_panel <- function(panel_df, curves, mat_names) {
  tenor_suffix <- sub("^X", "", mat_names)

  setNames(lapply(curves, function(curve_name) {
    curve_cols <- paste0(curve_name, ".", tenor_suffix)
    curve_df <- data.frame(
      time = as.Date(panel_df$time),
      panel_df[, curve_cols, drop = FALSE],
      check.names = FALSE
    )
    colnames(curve_df) <- c("time", mat_names)
    curve_df
  }), curves)
}

interp_cc_yield <- function(curve_row, target_maturity, mats, mat_names) {
  target_maturity <- as.numeric(target_maturity)

  if (length(target_maturity) != 1 || is.na(target_maturity) || target_maturity <= 0) {
    stop("`target_maturity` must be a positive scalar measured in years.")
  }

  node_years <- mats / 12
  zero_rates <- as.numeric(curve_row[1, mat_names, drop = TRUE]) / 100
  log_discount_nodes <- -zero_rates * node_years
  log_discount_curve <- stats::splinefun(
    x = node_years,
    y = log_discount_nodes,
    method = "monoH.FC"
  )

  as.numeric(-log_discount_curve(target_maturity) / target_maturity)
}

cc_discount_factor <- function(rate, maturity) {
  exp(-rate * maturity)
}

format_shock_label <- function(shock_run_spec) {
  if (!is.null(shock_run_spec$label)) {
    return(shock_run_spec$label)
  }

  paste(
    paste(shock_run_spec$shock_curves, collapse = "+"),
    paste(shock_run_spec$shock_factors, collapse = "+"),
    scales::number(shock_run_spec$shock_magnitude, accuracy = 0.001, trim = TRUE),
    sep = " "
  )
}

curve_yield_list_to_panels <- function(curve_yields, curves, mat_names) {
  setNames(lapply(curves, function(curve_name) {
    curve_df <- curve_yields[[curve_name]] %>%
      dplyr::mutate(time = as.Date(time)) %>%
      dplyr::arrange(time)
    colnames(curve_df) <- c("time", mat_names)
    curve_df
  }), curves)
}

dly_propagated_full_yields <- function(propagated_fit_obj, baseline_fit_obj,
                                       curves = propagated_fit_obj$curves) {
  setNames(lapply(curves, function(curve_name) {
    propagated_beta <- propagated_fit_obj$country_betas$global[[curve_name]] +
      baseline_fit_obj$country_betas$idiosyncratic[[curve_name]]

    yield_hat <- propagated_beta %*% propagated_fit_obj$single_curve[[curve_name]]$phi$phi
    curve_df <- data.frame(
      time = propagated_fit_obj$single_curve[[curve_name]]$time,
      as.data.frame(yield_hat)
    )
    colnames(curve_df) <- c("time", propagated_fit_obj$single_curve[[curve_name]]$yield_names)
    curve_df
  }), curves)
}

collect_curve_snapshots <- function(scenarios, mats, mat_names) {
  purrr::imap_dfr(scenarios, function(scenario_obj, scenario_key) {
    purrr::imap_dfr(scenario_obj$curve_snapshots, function(curve_row, curve_name) {
      tibble::tibble(
        scenario = scenario_obj$name,
        model = scenario_obj$model,
        scenario_type = scenario_obj$scenario_type,
        shock_label = scenario_obj$shock_label,
        curve = curve_name,
        maturity_months = mats,
        zero_rate = as.numeric(curve_row[1, mat_names, drop = TRUE]) / 100
      )
    })
  })
}

price_tontine_ladder <- function(curve_snapshots, tontine_schedule, country_weights,
                                 mats, mat_names, scenario_name, model_name,
                                 scenario_type = "baseline", shock_label = NA_character_) {
  purrr::imap_dfr(curve_snapshots, function(curve_row, curve_name) {
    country_weight <- country_weights[[curve_name]]

    tibble::tibble(
      scenario = scenario_name,
      model = model_name,
      scenario_type = scenario_type,
      shock_label = shock_label,
      period = tontine_schedule$period,
      year = tontine_schedule$year,
      T_k = tontine_schedule$T_k,
      tau_years = tontine_schedule$tau_years,
      q_k = tontine_schedule$q_k,
      p_k = tontine_schedule$p_k,
      country = curve_name,
      country_weight = country_weight,
      zero_rate = purrr::map_dbl(tontine_schedule$tau_years, function(tau_k) {
        interp_cc_yield(curve_row, tau_k, mats, mat_names)
      }),
      discount_factor = purrr::map_dbl(tontine_schedule$tau_years, function(tau_k) {
        cc_discount_factor(
          rate = interp_cc_yield(curve_row, tau_k, mats, mat_names),
          maturity = tau_k
        )
      }),
      country_scheduled_cash_flow = country_weight * tontine_schedule$pool_scheduled_payout,
      country_expected_cash_flow = country_weight * tontine_schedule$pool_expected_payout,
      rung_purchase_cost = country_expected_cash_flow * discount_factor
    )
  })
}

summarize_ladder_outputs <- function(country_ladder) {
  rung_summary <- country_ladder %>%
    dplyr::group_by(scenario, model, scenario_type, shock_label, period, year, T_k) %>%
    dplyr::summarise(
      scheduled_pool_payout = sum(country_scheduled_cash_flow),
      expected_pool_payout = sum(country_expected_cash_flow),
      rung_purchase_cost = sum(rung_purchase_cost),
      .groups = "drop"
    )

  list(
    rung_summary = rung_summary
  )
}

build_ladder_scenario <- function(curve_panels, curve_snapshots, tontine_schedule,
                                  country_weights, mats, mat_names, scenario_name,
                                  model_name, scenario_type = "baseline",
                                  shock_label = NA_character_, metadata = list()) {
  country_ladder <- price_tontine_ladder(
    curve_snapshots = curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = scenario_name,
    model_name = model_name,
    scenario_type = scenario_type,
    shock_label = shock_label
  )

  ladder_summary <- summarize_ladder_outputs(country_ladder)

  list(
    name = scenario_name,
    model = model_name,
    scenario_type = scenario_type,
    shock_label = shock_label,
    curve_panels = curve_panels,
    curve_snapshots = curve_snapshots,
    country_ladder = country_ladder,
    rung_summary = ladder_summary$rung_summary,
    metadata = metadata
  )
}

fit_dns_curves <- function(yields_window, curves, mats, mat_names, lambdas, cutoffs, valuation_date) {
  dns_fit <- st_prepare_single_curve_state(
    yields = yields_window,
    lambdas = lambdas,
    cutoffs = cutoffs,
    curves = curves,
    mats = mats
  )

  curve_panels <- setNames(lapply(curves, function(curve_name) {
    curve_fit_to_panel(
      time_index = dns_fit$time,
      fitted_matrix = dns_fit$bl_yields$nsfit[[curve_name]]$NSfit,
      mat_names = mat_names
    )
  }), curves)

  list(
    fit = dns_fit,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves)
  )
}

fit_dns_shocked_curves <- function(dns_fit_obj, curves, mat_names, valuation_date, shock_run_spec) {
  shocked_fit_obj <- st_dns_shock_from_single_curve_state(
    single_curve_state = dns_fit_obj,
    shock_curves = shock_run_spec$shock_curves,
    shock_factors = shock_run_spec$shock_factors,
    shock_magnitude = shock_run_spec$shock_magnitude,
    shock_type = shock_run_spec$shock_type,
    shock_window = shock_run_spec$shock_window
  )

  curve_panels <- curve_yield_list_to_panels(shocked_fit_obj$yields, curves, mat_names)

  list(
    fit = shocked_fit_obj,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves),
    shock_label = format_shock_label(shock_run_spec)
  )
}

fit_dly_curves <- function(yields_window, curves, mats, lambdas, reference_curve,
                           valuation_date,
                           component = c("raw", "global", "idiosyncratic", "propagated_full"),
                           mat_names) {
  component <- match.arg(component)

  dly_fit_obj <- dly_fit(
    yields = yields_window,
    mats = mats,
    lambdas = lambdas,
    curves = curves,
    reference = reference_curve
  )

  curve_yields <- switch(
    component,
    propagated_full = dly_propagated_full_yields(dly_fit_obj, dly_fit_obj, curves),
    dly_fit_obj$yields[[component]][curves]
  )
  curve_panels <- curve_yield_list_to_panels(curve_yields, curves, mat_names)

  list(
    fit = dly_fit_obj,
    component = component,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves)
  )
}

fit_dly_shocked_curves <- function(dly_fit_obj, curves, mat_names, valuation_date,
                                   shock_run_spec,
                                   component = c("raw", "global", "idiosyncratic", "propagated_full")) {
  component <- match.arg(component)

  shocked_fit_obj <- st_dly_shock_from_fit(
    dly_fit_obj = dly_fit_obj,
    shock_curves = shock_run_spec$shock_curves,
    shock_factors = shock_run_spec$shock_factors,
    shock_magnitude = shock_run_spec$shock_magnitude,
    shock_type = shock_run_spec$shock_type,
    shock_window = shock_run_spec$shock_window
  )

  curve_yields <- switch(
    component,
    propagated_full = dly_propagated_full_yields(shocked_fit_obj$fit, dly_fit_obj, curves),
    shocked_fit_obj$fit$yields[[component]][curves]
  )
  curve_panels <- curve_yield_list_to_panels(curve_yields, curves, mat_names)

  list(
    fit = shocked_fit_obj$fit,
    shock_fit = shocked_fit_obj,
    component = component,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves),
    shock_label = format_shock_label(shock_run_spec)
  )
}

fit_mce_curves <- function(yields_window, curves, mats, lambdas, cutoffs, reference_curve,
                           valuation_date, mce_run_spec, mat_names) {
  mce_fit_obj <- mc_fit_shock_baseline(
    yields = yields_window,
    lambdas = lambdas,
    cutoffs = cutoffs,
    reference = reference_curve,
    curves = curves,
    mats = mats,
    X_trunc = mce_run_spec$x_trunc,
    Xt_smooth = mce_run_spec$xt_smooth,
    smoother = mce_run_spec$smoother,
    hp_lambda = mce_run_spec$hp_lambda,
    CR_S0_shrink_diag = mce_run_spec$cov_shrink_diag
  )

  curve_panels <- split_curve_panel(mce_fit_obj$baseline_fit$curve, curves, mat_names)

  list(
    fit = mce_fit_obj,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves)
  )
}

fit_mce_shocked_curves <- function(mce_fit_obj, curves, mat_names, valuation_date, shock_run_spec) {
  shocked_fit_obj <- mc_fit_shock_from_baseline(
    baseline_state = mce_fit_obj,
    shock_curves = shock_run_spec$shock_curves,
    shock_factors = shock_run_spec$shock_factors,
    shock_magnitude = shock_run_spec$shock_magnitude,
    shock_type = shock_run_spec$shock_type,
    shock_window = shock_run_spec$shock_window,
    reuse_BS0 = shock_run_spec$reuse_BS0,
    reuse_ECM = shock_run_spec$reuse_ECM
  )

  curve_panels <- split_curve_panel(shocked_fit_obj$shocked_curve, curves, mat_names)

  list(
    fit = shocked_fit_obj,
    curve_panels = curve_panels,
    curve_snapshots = extract_curve_snapshot_list(curve_panels, valuation_date, curves),
    shock_label = format_shock_label(shock_run_spec)
  )
}

bind_scenario_component <- function(scenarios, component) {
  dplyr::bind_rows(lapply(scenarios, `[[`, component))
}
```

```{r stage1-window}
valuation_date <- first_window_date(yields[[reference_curve]], valuation_year)
estimation_end <- valuation_date

estimation_yields <- filter_estimation_window(
  yields = yields,
  start_date = estimation_start,
  end_date = estimation_end
)

```

```{r stage1-schedule}
payout_dates <- as.Date(vapply(payout_years, function(year_value) {
  as.character(first_window_date(yields[[reference_curve]], year_value))
}, character(1)))

p <- c(cumprod(1 - q))[seq_along(q)]
payout_per_member <- rep(target_total_payout_per_member / n_rungs, n_rungs)
pool_scheduled_payout <- N_members * payout_per_member
pool_expected_payout <- p * pool_scheduled_payout
tau_years <- as.numeric(payout_dates - valuation_date) / 365.25

tontine_schedule <- tibble::tibble(
  period = seq_len(n_rungs),
  year = payout_years,
  T_k = payout_dates,
  tau_years = tau_years,
  q_k = q,
  p_k = p,
  payout_per_member = payout_per_member,
  pool_scheduled_payout = pool_scheduled_payout,
  pool_expected_payout = pool_expected_payout
)
```

```{r baseline-curves}
dns_baseline <- fit_dns_curves(
  yields_window = estimation_yields,
  curves = curves,
  mats = mats,
  mat_names = mat_names,
  lambdas = lambdas,
  cutoffs = cutoffs,
  valuation_date = valuation_date
)

dly_baseline <- fit_dly_curves(
  yields_window = estimation_yields,
  curves = curves,
  mats = mats,
  lambdas = lambdas,
  reference_curve = reference_curve,
  valuation_date = valuation_date,
  component = dly_component,
  mat_names = mat_names
)

mce_baseline <- fit_mce_curves(
  yields_window = estimation_yields,
  curves = curves,
  mats = mats,
  lambdas = lambdas,
  cutoffs = cutoffs,
  reference_curve = reference_curve,
  valuation_date = valuation_date,
  mce_run_spec = mce_run_spec,
  mat_names = mat_names
)
```

```{r stage1-scenarios}
stage1_baseline_scenarios <- list(
  dns = build_ladder_scenario(
    curve_panels = dns_baseline$curve_panels,
    curve_snapshots = dns_baseline$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = "Baseline DNS",
    model_name = "DNS",
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end
    )
  ),
  dly = build_ladder_scenario(
    curve_panels = dly_baseline$curve_panels,
    curve_snapshots = dly_baseline$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = "Baseline DLY",
    model_name = "DLY",
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end,
      dly_component = dly_component
    )
  ),
  mce = build_ladder_scenario(
    curve_panels = mce_baseline$curve_panels,
    curve_snapshots = mce_baseline$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = "Baseline MCE",
    model_name = "MCE",
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end,
      mce_run_spec = mce_run_spec
    )
  )
)
```

```{r stage2-scenarios}
stage2_shocked_scenarios <- list()

for (shock_key in names(shock_specs)) {
  shock_spec <- shock_specs[[shock_key]]

  dns_shocked <- fit_dns_shocked_curves(
    dns_fit_obj = dns_baseline$fit,
    curves = curves,
    mat_names = mat_names,
    valuation_date = valuation_date,
    shock_run_spec = shock_spec
  )

  dly_shocked <- fit_dly_shocked_curves(
    dly_fit_obj = dly_baseline$fit,
    curves = curves,
    mat_names = mat_names,
    valuation_date = valuation_date,
    shock_run_spec = shock_spec,
    component = dly_component
  )

  mce_shocked <- fit_mce_shocked_curves(
    mce_fit_obj = mce_baseline$fit,
    curves = curves,
    mat_names = mat_names,
    valuation_date = valuation_date,
    shock_run_spec = shock_spec
  )

  stage2_shocked_scenarios[[paste0("dns_", shock_key)]] <- build_ladder_scenario(
    curve_panels = dns_shocked$curve_panels,
    curve_snapshots = dns_shocked$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = paste("DNS", dns_shocked$shock_label),
    model_name = "DNS",
    scenario_type = "shock",
    shock_label = dns_shocked$shock_label,
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end,
      shock_run_spec = shock_spec
    )
  )

  stage2_shocked_scenarios[[paste0("dly_", shock_key)]] <- build_ladder_scenario(
    curve_panels = dly_shocked$curve_panels,
    curve_snapshots = dly_shocked$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = paste("DLY", dly_shocked$shock_label),
    model_name = "DLY",
    scenario_type = "shock",
    shock_label = dly_shocked$shock_label,
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end,
      dly_component = dly_component,
      shock_run_spec = shock_spec
    )
  )

  stage2_shocked_scenarios[[paste0("mce_", shock_key)]] <- build_ladder_scenario(
    curve_panels = mce_shocked$curve_panels,
    curve_snapshots = mce_shocked$curve_snapshots,
    tontine_schedule = tontine_schedule,
    country_weights = country_weights,
    mats = mats,
    mat_names = mat_names,
    scenario_name = paste("MCE", mce_shocked$shock_label),
    model_name = "MCE",
    scenario_type = "shock",
    shock_label = mce_shocked$shock_label,
    metadata = list(
      valuation_date = valuation_date,
      estimation_start = estimation_start,
      estimation_end = estimation_end,
      mce_run_spec = mce_run_spec,
      shock_run_spec = shock_spec
    )
  )
}
```

```{r valuation-snapshot-comparison}
stage1_curve_snapshots <- collect_curve_snapshots(stage1_baseline_scenarios, mats, mat_names)
stage2_curve_snapshots <- collect_curve_snapshots(stage2_shocked_scenarios, mats, mat_names)
comparison_curve_snapshots <- dplyr::bind_rows(stage1_curve_snapshots, stage2_curve_snapshots) %>%
  dplyr::arrange(model, scenario_type, shock_label, curve, maturity_months)
```

```{r stage1-summaries}
stage1_rung_summary <- bind_scenario_component(stage1_baseline_scenarios, "rung_summary") %>%
  dplyr::arrange(model, period)
```

```{r shock-summaries}
stage2_rung_summary <- bind_scenario_component(stage2_shocked_scenarios, "rung_summary") %>%
  dplyr::arrange(model, period, shock_label)
```

```{r plots}
ggplot(stage1_rung_summary, aes(x = factor(year), y = rung_purchase_cost, color = model, group = model)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2) +
  scale_y_continuous(labels = dollar_format()) +
  labs(
    title = "Rung Purchase Cost by Baseline Model",
    x = "Payout Year",
    y = "Rung Purchase Cost"
  ) +
  theme_minimal()

ggplot(
  stage2_rung_summary,
  aes(x = factor(year), y = rung_purchase_cost, color = shock_label, group = shock_label)
) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2) +
  facet_wrap(~model, ncol = 3) +
  scale_y_continuous(labels = dollar_format()) +
  labs(
    title = "Stage-2 Shocked Rung Purchase Cost by Model",
    x = "Payout Year",
    y = "Rung Purchase Cost",
    color = "Shock Scenario"
  ) +
  theme_minimal()

ggplot(
  comparison_curve_snapshots %>%
    dplyr::filter(curve == "usa"),
  aes(x = maturity_months, y = 100 * zero_rate, color = scenario)
) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 1.4) +
  facet_wrap(~model, ncol = 3) +
  scale_x_continuous(breaks = mats) +
  labs(
    title = "USA Valuation-Date Zero Curves: Baseline vs Full-Window Factor Shocks",
    x = "Maturity (months)",
    y = "Zero Rate (%)",
    color = NULL
  ) +
  theme_minimal()
```
